---
title: "Data preparation"
format: html
editor: visual
---

Quarto document for data preparation. Code here is for subsetting herbivore data from the main fish dataset. The main fish dataset is not shared in this repository as other colleagues are using the data for their respective works.

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(iNEXT)
```

# Read csv

```{r}
db_master <- read_csv("Data/master_ROV_fish_Tim_2.csv",
                  trim_ws = TRUE)

#glimpse(db_master)
```

## ABUNDANCE

### Select relevant columns

```{r}
fg_abun <- db_master |>
  filter(Family != "Chanidae" & # remove families mislabelled as herbivores
           Family != "Ostraciidae" &
           Family != "Pomacentridae" &
           Family != "Tetraodontidae") |> 
  select(Reef_2,
         Site,
         Transect,
         Number,
         Depth_m,
         Habitat,
         Aspect_descriptive,
         Functional.Group,
         Benthic_Complexity)
```

### Wide to long data format and select relevant functional groups

```{r}
fg_abun_wide <-
fg_abun |> pivot_wider(names_from = Functional.Group, # wide format to account for 0 values
                          values_from = Number,
                          values_fn = sum) |> 
  select(Reef_2,
         Site, 
         Transect,
         Depth_m,
         Habitat,
         Aspect_descriptive,
         Benthic_Complexity,
         `cropper/grazer`,
         browser,
         detritivore,
         excavator,
         scraper) |> 
  rename(cropper = `cropper/grazer`) |> # simplify cropper name
  mutate(Habitat = recode(Habitat,
                          bommie = "lagoon",
                          outer_reef = "outer_slope"),
         Benthic_Complexity = recode(Benthic_Complexity,
                                     "1.5" = 2,
                                     "2.5" = 3,
                                     "3.5" = 4),
         across(cropper: scraper, 
                ~replace_na(.x, 0))) # replace na with 0
```

#### Export abundance csv

```{r}
db_abun <- write.csv(fg_abun_wide, file = "Exported_Data/herb_abundance.csv")
```

## BIOMASS

### Select relevant columns and remove families mislabelled as herbivores

```{r}
fg_biom_long <- db_master |>  
  filter(Family != "Chanidae" & # remove families mislabelled as herbivores
           Family != "Ostraciidae" &
           Family != "Pomacentridae" &
           Family != "Tetraodontidae") |> 
  select(Reef_2,
         Site,
         Transect,
         #Genus,
         #Species,
         #Number,
         Length_cm,
         #Biomass.Constant.A,
         #Biomass.Constant.B,
         Biomass_G,
         Depth_m,
         Habitat,
         Aspect_descriptive,
         Functional.Group,
         Benthic_Complexity)|> 
  filter(Biomass_G != "NA") # remove NA values (those that dont have size estimates)
```

### Long to wide format

```{r}
fg_biom_wide <-
fg_biom_long |> 
  group_by(Reef_2,
           Site, 
           Transect, 
           Depth_m,
           Aspect_descriptive,
           Functional.Group,
           Habitat,
           Benthic_Complexity) |> 
  summarise(Biomass_KG = sum(Biomass_G)/1000) |> 
  ungroup() |>
  #mutate(Biomass_KG = S_Biomass_G/1000) |> 
  pivot_wider(names_from = Functional.Group, # wide format to account for 0 values
                          values_from = Biomass_KG,
                          values_fn = sum,
                          values_fill = 0) |>  
  select(Reef_2,
         Site, 
         Transect,
         Depth_m,
         Habitat,
         Aspect_descriptive,
         Benthic_Complexity,
         `cropper/grazer`,
         browser,
         detritivore,
         excavator,
         scraper) |> 
  rename(cropper = `cropper/grazer`) |> # simplify cropper name
  mutate(Habitat = recode(Habitat,
                          bommie = "lagoon",
                          outer_reef = "outer_slope"),
         Benthic_Complexity = recode(Benthic_Complexity,
                                    # "1.5" = 2,
                                     "2.5" = 3,
                                     "3.5" = 4))
```

#### Export biomass csv

```{r}
db_biom <- write.csv(fg_biom_wide, "Exported_Data/herb_biomass.csv")
```

## SPECIES RICHNESS

### Database for iNEXT analysis

```{r}
fg_sprich <- db_master |> 
  filter(Functional.Group == "browser" |
           Functional.Group == "cropper/grazer" |
           Functional.Group == "detritivore" |
           Functional.Group == "excavator" |
           Functional.Group == "scraper") |> 
  filter(Family != "Chanidae" & # remove families mislabelled as herbivores
           Family != "Ostraciidae" &
           Family != "Pomacentridae" &
           Family != "Tetraodontidae") |> 
  select(Reef_2,
         Site,
         Transect,
         Binomial,
         Number,
         Depth_m,
         Habitat,
         Aspect_descriptive,
         Functional.Group,
         Benthic_Complexity) |> 
  mutate(Habitat = recode(Habitat,
                          bommie = "lagoon",
                          outer_reef = "outer_slope"),
        New_ID = factor(paste(Reef_2,
                               Site,
                               Transect,
                               Depth_m,
                               Habitat,
                               Aspect_descriptive,
                               Benthic_Complexity,
                               sep = "|")))
```

### Species per site, depth, slope, habitat

```{r}
sp_count <-
  fg_sprich |> 
  group_by(New_ID, 
           Binomial) |> 
  dplyr::summarise(Count = sum(Number)) |> 
  ungroup()
```

#### Long to wide format

```{r}
sp_count_wide <- 
sp_count |> 
  pivot_wider(names_from = Binomial,
              values_from = Count,
              values_fill = 0) 
```

#### Remove column names cause iNEXT wont run with categorical

```{r}
sp_count_wide_v2 <-
sp_count_wide |> 
  column_to_rownames("New_ID") |> 
  t() # transpose to make site columns and species rows
```

##### run iNEXT

```{r}
sprich_inext <- sp_count_wide_v2 |> 
  iNEXT(q = c(0, 1),
        datatype = "abundance",
        endpoint = 1000,
        nboot = 100)

#sprich_inext$AsyEst
```

### Separate species richness only

```{r}
spr_asym <- sprich_inext$AsyEst |> 
  filter(Diversity == "Species richness")
```

### Split ID column to separate variable columns

```{r}
spr_asym_wide <- 
spr_asym |> 
  separate_wider_delim(Assemblage,
                       delim = "|",
                       names = c("Reef_2",
                                 "Site",
                                 "Transect",
                                 "Depth_m",
                                 "Habitat",
                                 "Aspect",
                                 "Benthic_Complexity")) |> 
  mutate(Site = factor(Site),
         Habitat = factor(Habitat),
         Aspect = factor(Aspect),
         Depth_m = as.numeric(Depth_m))
```

#### export sprich csv

```{r}
db_spr_asym <- write.csv(spr_asym_wide, "Exported_Data/herb_sprich.csv")
```

## ASSEMBLAGES

```{r}
fg_assem <- 
  db_master |> 
  filter(Family != "Chanidae" & # remove families mislabelled as herbivores
           Family != "Ostraciidae" &
           Family != "Pomacentridae" &
           Family != "Tetraodontidae") |> 
  select(Reef_2,
        Site,
        # Transect,
         Genus,
         Species,
         Number,
         Depth_m,
         Habitat,
         Aspect_descriptive,
         Functional.Group,
        Benthic_Complexity) |> 
    filter(Functional.Group == "browser" |
           Functional.Group == "cropper/grazer" |
           Functional.Group == "detritivore" |
           Functional.Group == "excavator" |
           Functional.Group == "scraper") |> 
  mutate(Benthic_Complexity = recode(Benthic_Complexity,
                                     "1.5" = 2,
                                     "2.5" = 3,
                                     "3.5" = 4)) |> 
  mutate(Species_2 = factor(paste(Genus, # make one column for species 
                                  Species, 
                                  sep = "_")),
         Depth_group = factor(case_when(Depth_m < 30 ~ "Shallow",
                                        Depth_m >= 30 & Depth_m < 60 ~ "Upper_mesophotic",
                                        Depth_m >=60 & Depth_m < 100 ~ "Lower_mesophotic" )),
         Slope_group = factor(case_match(Aspect_descriptive,
                                         "flat" ~ "Flat",
                                         "wall" ~ "Wall",
                                         c("gentle_slope",
                                           "moderate_slope",
                                           "steep_slope") ~ "Slope")))
```

## Group according to site, depth, slope

```{r}
fg_assem_v2 <- 
fg_assem |> 
  group_by(Species_2,
           Depth_group,
           Slope_group, 
           Reef_2,
           Site,
           Habitat,
           Aspect_descriptive,
           Benthic_Complexity) |> 
  summarise(Sum = sum(Number)) |> 
  ungroup()
```

## Long tow to wide format

```{r}
fg_assem_wide <- 
fg_assem_v2 |> pivot_wider(names_from = Species_2, # wide format to account for 0 values
                          values_from = Sum,
                          values_fn = sum,
                        values_fill = 0)
```

### Export assem csv

```{r}
db_assem <- write.csv(fg_assem_wide, file = "Exported_Data/herb_assem.csv")
```
