---
title: "Data preparation"
format: html
editor: visual
---

Quarto document for data preparation 

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(iNEXT)
```

# Read csv

```{r}
db_master <- read_csv("Data/master_ROV_fish_Tim_2.csv",
                  trim_ws = TRUE)

glimpse(db_master)
```

## Abundance

### Select relevant columns

```{r}
fg_abun <- db_master |>
  filter(Family != "Chanidae" & # remove families mislabelled as herbivores
           Family != "Ostraciidae" &
           Family != "Pomacentridae" &
           Family != "Tetraodontidae") |> 
  select(Site,
         Transect,
         Number,
         Depth_m,
         Habitat,
         Aspect_descriptive,
         Functional.Group)
```

### Wide to long data format and select relevant functional groups

```{r}
fg_abun_wide <-
fg_abun |> pivot_wider(names_from = Functional.Group, # wide format to account for 0 values
                          values_from = Number,
                          values_fn = sum) |> 
  select(Site, 
         Transect,
         Depth_m,
         Habitat,
         Aspect_descriptive,
         `cropper/grazer`,
         browser,
         detritivore,
         excavator,
         scraper) |> 
  rename(cropper = `cropper/grazer`) |> # simplify cropper name
  mutate(Habitat = recode(Habitat,
                          bommie = "lagoon",
                          outer_reef = "outer_slope"),
         across(cropper: scraper, 
                ~replace_na(.x, 0))) # replace na with 0
```

#### Export abundance csv

```{r}
db_abun <- write.csv(fg_abun_wide, "herb_abundance.csv")
```

## Biomass

```{r}
glimpse(db_master)
```


### Select relevant columns and remove families mislabelled as herbivores

```{r}
fg_biom_long <- db_master |>  
  filter(Family != "Chanidae" & # remove families mislabelled as herbivores
           Family != "Ostraciidae" &
           Family != "Pomacentridae" &
           Family != "Tetraodontidae") |> 
  select(Site,
         Transect,
         #Genus,
         #Species,
         #Number,
         Length_cm,
         #Biomass.Constant.A,
         #Biomass.Constant.B,
         Biomass_G,
         Depth_m,
         Habitat,
         Aspect_descriptive,
         Functional.Group) |> 
  filter(Biomass_G != "NA") # remove NA values (those that dont have size estimates)
```
mutate(across(Biomass_G,
                  ~replace_na(.x, 0))) |> 

### Long to wide format

```{r}
fg_biom_wide <-
fg_biom_long |> 
  group_by(Site, 
           Transect, 
           Depth_m,
           Aspect_descriptive,
           Functional.Group,
           Habitat) |> 
  summarise(Biomass_KG = sum(Biomass_G)/1000) |> 
  ungroup() |>
  #mutate(Biomass_KG = S_Biomass_G/1000) |> 
  pivot_wider(names_from = Functional.Group, # wide format to account for 0 values
                          values_from = Biomass_KG,
                          values_fn = sum,
                          values_fill = 0) |>  
  select(Site, 
         Transect,
         Depth_m,
         Habitat,
         Aspect_descriptive,
         `cropper/grazer`,
         browser,
         detritivore,
         excavator,
         scraper) |> 
  rename(cropper = `cropper/grazer`) |> # simplify cropper name
  mutate(Habitat = recode(Habitat,
                          bommie = "lagoon",
                          outer_reef = "outer_slope"))
```

#### Export biomass csv

```{r}
db_biom <- write.csv(fg_biom_wide, "herb_biomass.csv")
```

## Species richness

database for iNEXT analysis

```{r}
fg_sprich <- db_master |> 
  filter(Functional.Group == "browser" |
           Functional.Group == "cropper/grazer" |
           Functional.Group == "detritivore" |
           Functional.Group == "excavator" |
           Functional.Group == "scraper") |> 
  filter(Family != "Chanidae" & # remove families mislabelled as herbivores
           Family != "Ostraciidae" &
           Family != "Pomacentridae" &
           Family != "Tetraodontidae") |> 
  select(Site,
         Transect,
         Binomial,
         Number,
         Depth_m,
         Habitat,
         Aspect_descriptive,
         Functional.Group) |> 
  mutate(Habitat = recode(Habitat,
                          bommie = "lagoon",
                          outer_reef = "outer_slope"),
        New_ID = factor(paste(Site,
                               Transect,
                               Depth_m,
                               Habitat,
                               Aspect_descriptive,
                               sep = "|")))
```

### species per site, depth, slope, habitat

```{r}
sp_count <-
  fg_sprich |> 
  group_by(New_ID, 
           Binomial) |> 
  dplyr::summarise(Count = sum(Number)) |> 
  ungroup()
```

### Long to wide format

```{r}
sp_count_wide <- 
sp_count |> 
  pivot_wider(names_from = Binomial,
              values_from = Count,
              values_fill = 0) 
```

### Remove column names cause iNEXT wont run with categorical

```{r}
sp_count_wide_v2 <-
sp_count_wide |> 
  column_to_rownames("New_ID") |> 
  t() # transpose to make site columns and species rows
```

### run iNEXT

```{r}
sprich_inext <- sp_count_wide_v2 |> 
  iNEXT(q = c(0, 1),
        datatype = "abundance",
        endpoint = 1000,
        nboot = 100)

#sprich_inext$AsyEst
```

### Separate species richness only

```{r}
spr_asym <- sprich_inext$AsyEst |> 
  filter(Diversity == "Species richness")
```

### Separate ID column to separate variable columns

```{r}
spr_asym_wide <- 
spr_asym |> 
  separate_wider_delim(Assemblage,
                       delim = "|",
                       names = c("Site",
                                 "Transect",
                                 "Depth_m",
                                 "Habitat",
                                 "Aspect")) |> 
  mutate(Site = factor(Site),
         Habitat = factor(Habitat),
         Aspect = factor(Aspect),
         Depth_m = as.numeric(Depth_m))
```

#### export sprich csv

```{r}
db_spr_asym <- write.csv(spr_asym_wide, "herb_sprich.csv")
```

## Assemblage

```{r}
fg_assem <- 
  db_master |> 
  filter(Family != "Chanidae" & # remove families mislabelled as herbivores
           Family != "Ostraciidae" &
           Family != "Pomacentridae" &
           Family != "Tetraodontidae") |> 
  select(Site,
        # Transect,
         Genus,
         Species,
         Number,
         Depth_m,
         Aspect_descriptive,
         Functional.Group) |> 
    filter(Functional.Group == "browser" |
           Functional.Group == "cropper/grazer" |
           Functional.Group == "detritivore" |
           Functional.Group == "excavator" |
           Functional.Group == "scraper") |> 
  mutate(Species_2 = factor(paste(Genus, # make one column for species 
                                  Species, 
                                  sep = "_")),
         Depth_group = factor(case_when(Depth_m < 30 ~ "Shallow",
                                        Depth_m >= 30 & Depth_m < 60 ~ "Upper_mesophotic",
                                        Depth_m >=60 & Depth_m < 100 ~ "Lower_mesophotic" )),
         Slope_group = factor(case_match(Aspect_descriptive,
                                         "flat" ~ "Flat",
                                         "wall" ~ "Wall",
                                         c("gentle_slope",
                                           "moderate_slope",
                                           "steep_slope") ~ "Slope")))
```

## Group according to site, depth, slope

```{r}
fg_assem_v2 <- 
fg_assem |> 
  group_by(Species_2,
           Depth_group,
           Slope_group, 
           Site,
           Aspect_descriptive) |> 
  summarise(Sum = sum(Number)) |> 
  ungroup()
```

## Long tow to wide format

```{r}
fg_assem_wide <- 
fg_assem_v2 |> pivot_wider(names_from = Species_2, # wide format to account for 0 values
                          values_from = Sum,
                          values_fn = sum,
                        values_fill = 0)
```

### export assem csv

```{r}
db_assem <- write.csv(fg_assem_wide, "herb_assem.csv")
```
