---
title: "Sprich"
format: html
editor: visual
---

# Clean up

```{r}
rm(list=ls())
gc()
```

Quarto document for fitting species richness among depth bands and slope orientation using Bayesian and lognormal distribution. Habitat type and site are considered group level variables.

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
#library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(vegan)
library(BiodiversityR)
library(ggrepel)
```

# Read data

```{r}
sprich <- read_csv("Data/herb_sprich.csv",
                      trim_ws = TRUE)
#glimpse(sprich)
```

# Declare factors

```{r}
sprich <- sprich |> 
  mutate(Reef_2 = factor(Reef_2),
         Site = factor(Site),
         Aspect = factor(Aspect),
         Habitat = factor(Habitat),
         Benthic_Complexity = factor(Benthic_Complexity))
```

# Model fitting

## Define formula

```{r}
sprich_form <- bf(Estimator ~ 
       Depth_m +
       Aspect +
       Benthic_Complexity + 
       Habitat +
       (1 | Reef_2/Site),
                        family = lognormal())
```

## Data exploration

```{r}
sprich |> 
  summarise(log_med = log(median(Estimator)),
            log_mad = log(mad(Estimator))) 
```

## Weakly informative priors

```{r}
priors_sprich <- prior(normal(1.2, 1.3), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(student_t(3, 0, 1.3), class = "sigma") +
  prior(student_t(3, 0, 1.3), class = "sd")
```

## Prior only model

```{r}
prior_mod_sprich <- brm(sprich_form,
                    data = sprich,
                    prior = priors_sprich,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## Prior evaluation

```{r}
prior_mod_sprich |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

# Fit model

```{r}
#| cache: true
sprich_mod <- update(prior_mod_sprich,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

# Partial plots

```{r}
sprich_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots()
```

# Chain diagnostics

```{r}
# prep
par_sprich_mod <- sprich_mod |>  
  get_variables() |> 
  str_subset("^b_.*")

# trace
sprich_mod |> mcmc_plot(type = "trace",
                         par = par_sprich_mod)
 
# autocorr
sprich_mod |> mcmc_plot(type = "acf_bar",
                         par = par_sprich_mod)
  
# rhat
sprich_mod  |> mcmc_plot(type = "rhat_hist")

# ess
sprich_mod  |> mcmc_plot(type = "neff_hist")
```

# Residuals

```{r}
sprich_resids <- make_brms_dharma_res(sprich_mod)

# qqplot
sprich_resids |> testUniformity()

#residplot
sprich_resids |> plotResiduals(quantreg = TRUE)
```

# Save model

```{r}
save(sprich_mod, file = "Model_Output/sprich_mod.Rdata")
```
