---
title: "Sprich_results"
format: html
editor: visual
---

# Cleanup

```{r}
rm(list=ls())
gc()
```

Quarto document for interpreting and plotting species richness among depth bands, slope orientation, and benthic complexity

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
#library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(vegan)
library(BiodiversityR)
library(ggrepel)
```

# Load model and rawdata

```{r}
#model
load("Model_Output/sprich_mod.Rdata")

#rawdata
#used for plotting with newdata
sprich <- read_csv("Data/herb_sprich.csv",
                      trim_ws = TRUE)
```

# Summary table

```{r}
sprich_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # backtransform from logscale
  summarise_draws(median,
                  HDInterval::hdi,
                  Pl= ~mean(.x < 1), #exceedence prob
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 | # filter weak evidence (0.85)
           Pg > 0.85)
```

# Plots

## DEPTH

### Newdata for plotting depth

```{r}
sprich_newdata <- with(sprich,
                       data.frame(Depth_m = seq(min(Depth_m),
                                              max(Depth_m),
                                              length = 100)))
```

### Prep db for plotting

```{r, cache=TRUE}
sprich_pred_depth <- 
  sprich_mod |> 
  emmeans(~ Depth_m, 
          at = sprich_newdata, 
          type = "link",
          rg.limit = 12000) |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame() # DONE
```

### Plot depth

```{r}
p_sprich_depth <-
sprich_pred_depth |> 
  ggplot(aes(y = median,
             x = Depth_m)) +
    geom_point(data = sprich,
             aes(y = Estimator),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  scale_y_continuous(expression(Species~richness~(ind.150m^-2)),
                       limits = c(0, 30),
  breaks = seq(0, 30, by = 10)) +
  scale_x_continuous(name = "Depth (m)",
                     breaks = seq(0, 100, by = 20)) +
  theme_classic() +
     theme(axis.title.x=element_text(size = 15),
        axis.text.x=element_text(size = 12),
        axis.title.y=element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18)) +
  ggtitle("Total herbivores") +
  theme(legend.position = "none")
```

### add images

```{r}
p_sprich_depth <-
p_sprich_depth + geom_image(data = tibble(Depth_m = 90,
                            median = 29),
                            aes(image = ("Images/naso.png")),
                            size = 0.30) +
  geom_image(data = tibble(Depth_m = 90,
                            median = 23),
                            aes(image = ("Images/ctenochaetus.png")),
                            size = 0.30) +
  geom_image(data = tibble(Depth_m = 70,
                            median = 29),
                            aes(image = ("Images/scarus.png")),
                            size = 0.30) +
    geom_image(data = tibble(Depth_m = 70,
                            median = 23),
                            aes(image = ("Images/chlorurus.png")),
                            size = 0.30) +
  theme(legend.position = "none")
  
```

## SLOPE

### Newdata for plotting Slope

```{r}
sprich_slope <- sprich_mod |> 
  emmeans(~ Aspect, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame()
```

### Plot slope

```{r}
p_sprich_slope <- 
sprich_slope |> 
  ggplot(aes(x = Aspect,
             y = median)) +
  geom_pointrange(aes(ymin = lower,
                      ymax = upper),
                  shape = 21,
                  size = 1,
                  fatten = 3,
                  color = "#8AA17D",
                  fill = "#8AA17D") +
  scale_y_continuous(Species~richness~(ind.150m^-2),
                     limits = c(0, 8),
                     breaks = seq(0, 8, by = 2)) +
  scale_x_discrete(name = "Slope orientation",
                   labels = c("Flat",
                              "Gentle slope",
                              "Moderate slope",
                              "Steep slope",
                              "Wall")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 20,
                                 vjust = 0.90,
                                 hjust = 0.70,
                                 size = 12),
        axis.title = element_text(size = 15),
        axis.text.y = element_text(size = 12))
```

#### Pairwise slope

```{r}
sprich_mod |> emmeans(~ Aspect,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  mutate(Exp = exp(.value)) |> 
  dplyr::select(-.chain, 
                -.value,
                -.iteration) |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  rhat,
                  Pl = ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  dplyr::filter(Pl > 0.85 | 
           Pg > 0.85) 
```

##### Prepare db for contrasts

```{r}
sprich_slope_pair <- 
  sprich_mod |> emmeans(~ Aspect,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  summarise(median_hdci(exp(.value),
                        .width = c(0.85, 0.95))) 
```

##### Plot contrasts

```{r}
 p_sprich_slope_pair <- ggplot() + 
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = sprich_slope_pair |> filter(.width == 0.85),
                  linewidth = 1.7) +
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = sprich_slope_pair |> filter(.width == 0.95),
                  pch = 21,
                  size = 1.2,
                  fill = "#8AA17D",
                  linewidth = 0.7) +
  geom_hline(yintercept = 1, 
             linetype = "dashed",
             color = "red",
             linewidth = 1) +
    coord_flip() +
  theme_classic() +
  scale_x_discrete(name = "Constrast: slope orientation",
                   labels = function(x) gsub("_", " ", x)) +
  scale_y_continuous(name = "",
                   trans = scales::log2_trans(),
                   breaks = seq(0, 2.5, by = 0.5)) +
  ggtitle("Species richness") +
  theme(axis.title = element_text(size = 15),
        axis.text = element_text(size = 12),
        plot.title = element_text(size = 18))
```

## BENTHIC COMPLEXITY

### Newdata for plotting benthic complexity

```{r}
sprich_bc <- sprich_mod |> 
  emmeans(~ Benthic_Complexity, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame() 
```

### Plot bc

```{r}
p_sprich_bc <- 
sprich_bc |> 
  ggplot(aes(x = Benthic_Complexity,
             y = median)) +
  geom_pointrange(aes(ymin = lower,
                      ymax = upper),
                  shape = 21,
                  size = 1,
                  fatten = 3,
                  color = "#8AA17D",
                  fill = "#8AA17D") +
  scale_y_continuous(Species~richness~(ind.150m^-2),
                     limits = c(0, 8),
                     breaks = seq(0, 8, by = 2)) +
  #scale_x_discrete(name = "Slope orientation",
   #                labels = c("Flat",
    #                          "Gentle slope",
     #                         "Moderate slope",
      #                        "Steep slope",
       #                       "Wall")) +
  scale_x_discrete(name = "Benthic complexity") +
  theme_classic() +
  theme(axis.text.x = element_text(
                                 size = 12),
        axis.title = element_text(size = 15),
        axis.text.y = element_text(size = 12))
```

#### Pairwise bc

```{r}
sprich_mod |> 
  emmeans(~ Benthic_Complexity,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  mutate(Exp = exp(.value)) |> 
  dplyr::select(-.chain, 
                -.value,
                -.iteration) |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  rhat,
                  Pl = ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  dplyr::filter(Pl > 0.85 | 
           Pg > 0.85) 
```

##### Plot bc contrasts

```{r}
# prepare db
sprich_bc_pair <- 
  sprich_mod |> 
  emmeans(~ Benthic_Complexity,
          type = "link") |> 
  #subset(Habitat != "passage") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  summarise(median_hdci(exp(.value),
                        .width = c(0.85, 0.95))) |> 
  as.data.frame()

# plot   
 p_sprich_bc_pair <- 
   ggplot() + 
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = sprich_bc_pair |> filter(.width == 0.85),
                  linewidth = 1.7) +
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = sprich_bc_pair |> filter(.width == 0.95),
                  pch = 21,
                  size = 1.2,
                  fill = "#8AA17D",
                  linewidth = 0.7) +
  geom_hline(yintercept = 1, 
             linetype = "dashed",
             color = "red",
             linewidth = 1) +
    coord_flip() +
  theme_classic() +
  #scale_x_discrete(name = "Reef zone",
   #                labels = c("Inner reef",
    #                          "Lagoon",
     #                         "Outer reef")) +
   scale_x_discrete(name = "Contrast: benthic complexity",
                   labels = function(x) gsub("_", " ", x)) +
  scale_y_continuous(name = "Scaled effect size",
                   trans = scales::log2_trans(),
                   breaks = seq(0, 2, by = 0.5)) +
  #ggtitle("Species richness") +
  theme(axis.title = element_text(size = 15),
        axis.text = element_text(size = 12),
        plot.title = element_text(size = 18)) 

# save fig 
 ggsave("Figures/Fig. SX. sprich_bc_pair.jpeg",
       plot = p_sprich_bc_pair, 
       dpi = 600, 
       height = 5, 
       width = 8, 
       units = "in") 
```

##### Plot zone contrasts

```{r}
# prepare db
sprich_zone_pair <- 
  sprich_mod |> 
  emmeans(~ Habitat,
          type = "link") |> 
  subset(Habitat != "passage") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  summarise(median_hdci(exp(.value),
                        .width = c(0.85, 0.95))) |> 
  as.data.frame()

# plot  
 p_sprich_zone_pair <- 
   ggplot() + 
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = sprich_zone_pair |> filter(.width == 0.85),
                  linewidth = 1.7) +
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = sprich_zone_pair |> filter(.width == 0.95),
                  pch = 21,
                  size = 1.2,
                  fill = "#8AA17D",
                  linewidth = 0.7) +
  geom_hline(yintercept = 1, 
             linetype = "dashed",
             color = "red",
             linewidth = 1) +
    coord_flip() +
  theme_classic() +
   scale_x_discrete(name = "Contrast: reef zone",
                   labels = function(x) gsub("_", " ", x)) +
  scale_y_continuous(name = "Scaled effect size",
                   trans = scales::log2_trans(),
                   breaks = seq(0, 2, by = 0.5)) +
  #ggtitle("Species richness") +
  theme(axis.title = element_text(size = 15),
        axis.text = element_text(size = 12),
        plot.title = element_text(size = 18)) #+
   #labs(y = "Scaled effect size", x = "Contrast: reef zone")
```

## REEF ZONE

### Newdata for plotting reef zone

```{r}
sprich_zone <- sprich_mod |> 
  emmeans(~ Habitat, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame() |> 
  filter(Habitat != "passage") |> 
  mutate(Habitat = factor(Habitat,
                          levels = c("lagoon",
                                     "inner_reef",
                                     "outer_slope"))) |> 
  mutate(Habitat = recode(Habitat,
                          "inner_reef" = "inner reef",
                          "outer_slope" = "outer reef")) |> 
  as.data.frame()
```

### Plot zone

```{r}
p_sprich_zone <- 
sprich_zone |> 
  ggplot(aes(x = Habitat,
             y = median)) +
  geom_pointrange(aes(ymin = lower,
                      ymax = upper),
                  shape = 21,
                  size = 1,
                  fatten = 3,
                  color = "#8AA17D",
                  fill = "#8AA17D") +
  scale_y_continuous(Species~richness~(ind.150m^-2),
                     limits = c(0, 8),
                     breaks = seq(0, 8, by = 2)) +
  #scale_x_discrete(name = "Slope orientation",
   #                labels = c("Flat",
    #                          "Gentle slope",
     #                         "Moderate slope",
      #                        "Steep slope",
       #                       "Wall")) +
  theme_classic() +
  theme(axis.text.x = element_text(
                                 size = 12),
        axis.title = element_text(size = 15),
        axis.text.y = element_text(size = 12)) +
  xlab("Reef zone")
```

# Combine figs

```{r}
p_sprich_all <-
p_sprich_depth / 
  p_sprich_slope /
  p_sprich_bc /
  p_ord3 + plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 15))
```

# ggsave

```{r}
ggsave("Fig. X2. sprich.jpeg",
       plot = p_sprich_all, 
       dpi = 600, 
       height = 15, 
       width = 9, 
       units = "in")
```

# Combine figs

```{r}
p_sprich_zone <-
p_sprich_zone + p_sprich_zone_pair + 
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 15))
```

# ggsave

```{r}
ggsave("Figures/Fig. SX. sprich_zone.jpeg",
       plot = p_sprich_zone, 
       dpi = 600, 
       height = 5, 
       width = 8, 
       units = "in")
```
