---
title: "Biomass_model_fit"
format: html
editor: visual
---

# Cleanup

```{r}
rm(list=ls())
gc()
```

Quarto document for fitting biomass (in kg) among depth bands and slope orientation using Bayesian and hurdle lognormal distribution. Hurdle model was used to account for zeroes. Habitat type and site are considered group level variables.

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
#library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(vegan)
library(BiodiversityR)
library(ggrepel)
```

# Read data

```{r}
fg_biom <- read_csv("Data/herb_biomass.csv",
                      trim_ws = TRUE)
#glimpse(fg_biom)
```

# Declare factors

```{r}
fg_biom <- fg_biom |> 
  mutate(Reef_2 = factor(Reef_2),
         Site = factor(Site),
         Aspect_descriptive = factor(Aspect_descriptive),
         Benthic_Complexity = factor(Benthic_Complexity),
         Habitat = factor(Habitat),
         herbs = cropper + browser + detritivore + excavator + scraper) # all herbivore column
```

# Summarize

## Sum

```{r}
fg_biom |> 
  group_by(Aspect_descriptive) |> 
  summarise(sum_herbs = length(herbs),
            sum_brow = length(browser),
            sum_exc = length(excavator),
            sum_crop = length(cropper),
            sum_det = length(detritivore))
```

## Median

```{r}
fg_biom |> 
  group_by(Aspect_descriptive) |> 
  summarise(median_herbs = median(herbs),
            median_brow = median(browser),
            median_exc = median(excavator),
            median_crop = median(cropper),
            median_det = median(detritivore))
```

## Max

```{r}
fg_biom |> 
  group_by(Aspect_descriptive) |> 
  summarise(max_herbs = max(herbs),
            max_brow = max(browser),
            max_exc = max(excavator),
            max_crop = max(cropper),
            max_det = max(detritivore))
```

# Hurdle lognormal 

# ALL HERBIVORES

## define formula

```{r}
b_herbs_form_2 <- 
  bf(herbs ~ 
       Depth_m +
       Aspect_descriptive +
       Benthic_Complexity + 
       Habitat +
       (1 | Reef_2/Site),
     family = hurdle_lognormal())
```

## Examine priors needed

```{r}
get_prior(b_herbs_form_2, data = fg_biom)
```

## Data exploration

```{r}
fg_biom |> 
  group_by(Depth_m,
           Aspect_descriptive) |>
  summarise(log_median = log(median(herbs)),
            log_mad = log(mad(herbs))) |> 
  arrange(-log_median) |> 
  filter(log_median != "-Inf") |> 
  filter(log_mad != "-Inf")
```

## Weakly informative priors

```{r}
b_priors_herbs_2 <- prior(normal(2.7, 3), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(student_t(3, 0, 3), class = "sigma") +
  prior(student_t(3, 0, 3), class = "sd") +
  prior(beta(1, 1), class = "hu")
```

## Prior only model 

```{r}
b_prior_mod_herbs_2 <- brm(b_herbs_form_2,
                    data = fg_biom,
                    prior = b_priors_herbs_2,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

# Fit model

```{r}
#| cache: true
b_mod_herbs_2 <- update(b_prior_mod_herbs_2,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## Traceplots

```{r}
# prep
par_biom_mod <- b_mod_herbs_2 |>  
  get_variables() |> 
  str_subset("^b_.*")

# trace
b_mod_herbs_2 |> mcmc_plot(type = "trace",
                         par = par_biom_mod)
 
# autocorr
b_mod_herbs_2 |> mcmc_plot(type = "acf_bar",
                         par = par_biom_mod)
  
# rhat
b_mod_herbs_2  |> mcmc_plot(type = "rhat_hist")

# ess
b_mod_herbs_2  |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
b_mod_herbs_resids <- make_brms_dharma_res(b_mod_herbs_2)

# qqplot
b_mod_herbs_resids |> testUniformity()

#residplot
b_mod_herbs_resids |> plotResiduals(quantreg = FALSE)
```

#### Save model

```{r}
save(b_mod_herbs_2, file = "Model_Outputs/b_mod_herbs_2.Rdata")
```

# CROPPERS

## Define formula

```{r}
b_crop_form <-
bf(cropper ~ 
       Depth_m +
       Aspect_descriptive +
       Benthic_Complexity + 
       Habitat +
       (1 | Reef_2/Site),
     family = hurdle_lognormal())
```

## Data exploration

```{r}
fg_biom |> 
  group_by(Depth_m,
           Aspect_descriptive,
           Habitat,
           Benthic_Complexity) |>
  summarise(log_median = log(median(cropper)),
            log_mad = log(mad(cropper))) |> 
  arrange(log_median) |> 
  filter(log_median != "-Inf") |> 
  filter(log_mad != "-Inf")
```

## Weakly informative priors

```{r}
b_priors_crop <- prior(normal(1.9, 1.5), class = "Intercept") + #1.5, 0.5
  prior(normal(0, 1.2), class = "b") + # 3
  prior(student_t(3, 0, 1.5), class = "sigma") +
  prior(student_t(3, 0, 1.5), class = "sd") +
  prior(beta(1, 1), class = "hu")
```

## Prior model

```{r}
b_prior_crop_mod <- brm(b_crop_form,
                    data = fg_biom,
                    prior = b_priors_crop,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

# Fit model

```{r}
#| cache: true
b_mod_crop <- update(b_prior_crop_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## Traceplots

```{r}
# prep
par_crop_mod <- b_mod_crop |>  
  get_variables() |> 
  str_subset("^b_.*")

# trace
b_mod_crop |> mcmc_plot(type = "trace",
                         par = par_crop_mod)
 
# autocorr
b_mod_crop |> mcmc_plot(type = "acf_bar",
                         par = par_crop_mod)
  
# rhat
b_mod_crop  |> mcmc_plot(type = "rhat_hist")

# ess
b_mod_crop |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
b_mod_crop_resids <- make_brms_dharma_res(b_mod_crop)

# qqplot
b_mod_crop_resids  |> testUniformity()

#residplot
b_mod_crop_resids  |> plotResiduals(quantreg = FALSE)
```

#### Save model

```{r}
save(b_mod_crop, file = "Model_Outputs/b_mod_crop.Rdata")
```

# DETRITIVORES

## Define formula

```{r}
b_det_form <- 
  bf(detritivore ~ 
       Depth_m +
       Aspect_descriptive +
       Benthic_Complexity + 
       Habitat +
       (1 | Reef_2/Site),
     family = hurdle_lognormal())
```

## Data exploration

```{r}
fg_biom |> 
  group_by(Depth_m,
           Aspect_descriptive) |>
  summarise(log_median = log(median(detritivore)),
            log_mad = log(mad(detritivore))) |> 
  arrange(-log_median)
```

## Weakly informative prior

```{r}
b_priors_det <- prior(normal(1.1, 1), class = "Intercept") +
  prior(normal(0, 1.1), class = "b") +
  prior(student_t(3, 0, 1), class = "sigma") +
  prior(student_t(3, 0, 1), class = "sd") +
  prior(beta(1, 1), class = "hu")
```

## Prior model

```{r}
b_prior_mod_det <- brm(b_det_form,
                    data = fg_biom,
                    prior = b_priors_det,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

# Fit model

```{r}
#| cache: true
b_mod_det <- update(b_prior_mod_det,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## Traceplots

```{r}
# prep
b_par_det_mod <- b_mod_det |>  
  get_variables() |> 
  str_subset("^b_.*")

# trace
b_mod_det |> mcmc_plot(type = "trace",
                         par = b_par_det_mod)
 
# autocorr
b_mod_det |> mcmc_plot(type = "acf_bar",
                         par = b_par_det_mod)
  
# rhat
b_mod_det  |> mcmc_plot(type = "rhat_hist")

# ess
b_mod_det |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
b_mod_det_resids <- make_brms_dharma_res(b_mod_det)

# qqplot
b_mod_det_resids |> testUniformity()

#residplot
b_mod_det_resids |> plotResiduals(quantreg = FALSE)
```

#### Save model

```{r}
save(b_mod_det, file = "Model_Outputs/b_mod_det.Rdata")
```

# SCRAPERS

## Define formula

```{r}
b_scra_form <-
bf(scraper ~ 
        Depth_m +
       Aspect_descriptive +
       Benthic_Complexity + 
       Habitat +
       (1 | Reef_2/Site),
     family = hurdle_lognormal())
```

## Data exploration

```{r}
fg_biom |> 
  group_by(Depth_m,
           Aspect_descriptive) |>
  summarise(log_median = log(median(scraper)),
            log_mad = log(mad(scraper))) |> 
  arrange(log_median) |> 
  filter(log_median != "-Inf") |> 
  filter(log_mad != "-Inf")
```


## Weakly informative prior

```{r}
b_priors_scra <- prior(normal(2.3, 2.7), class = "Intercept") +
  prior(normal(0, 0.8), class = "b") +
  prior(student_t(3, 0, 2.7), class = "sigma") +
  prior(student_t(3, 0, 2.7), class = "sd") +
  prior(beta(1, 1), class = "hu")
```

## Prior model

```{r}
b_prior_mod_scra <- brm(b_scra_form,
                    data = fg_biom,
                    prior = b_priors_scra,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

# Fit model

```{r}
#| cache: true
b_mod_scra <- update(b_prior_mod_scra,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## Traceplots

```{r}
# prep
b_par_scra_mod <- b_mod_scra |>  
  get_variables() |> 
  str_subset("^b_.*")

# trace
b_mod_scra |> mcmc_plot(type = "trace",
                         par = b_par_scra_mod)
 
# autocorr
b_mod_scra |> mcmc_plot(type = "acf_bar",
                         par = b_par_scra_mod)
  
# rhat
b_mod_scra  |> mcmc_plot(type = "rhat_hist")

# ess
b_mod_scra |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
b_mod_scra_resids <- make_brms_dharma_res(b_mod_scra)

# qqplot
b_mod_scra_resids |> testUniformity()

#residplot
b_mod_scra_resids |> plotResiduals(quantreg = FALSE)
```

#### Save model

```{r}
save(b_mod_scra, file = "Model_Outputs/b_mod_scra.Rdata")
```

# EXCAVATORS

## Define formula

```{r}
b_exc_form <-
bf(excavator ~ 
       Depth_m +
       Aspect_descriptive +
       Benthic_Complexity + 
       Habitat +
       (1 | Reef_2/Site),
     family = hurdle_lognormal())
```

## Data exploration

```{r}
fg_biom |> 
  group_by(Depth_m,
           Aspect_descriptive) |>
  summarise(log_median = log(median(excavator)),
            log_mad = log(mad(excavator))) |> 
  arrange(-log_median) |> 
  filter(log_median != "-Inf") |> 
  filter(log_mad != "-Inf")
```

## Weakly informative prior

```{r}
b_priors_exc <- prior(normal(1.4, 1.8), class = "Intercept") +
  prior(normal(0, 0.7), class = "b") +
  prior(student_t(3, 0, 1.8), class = "sigma") +
  prior(student_t(3, 0, 1.8), class = "sd") +
  prior(beta(1, 1), class = "hu")
```

## Prior model

```{r}
b_prior_mod_exc <- brm(b_exc_form,
                    data = fg_biom,
                    prior = b_priors_exc,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

# Fit model

```{r}
#| cache: true
b_mod_exc <- update(b_prior_mod_exc,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## Traceplots

```{r}
# prep
b_par_exc_mod <- b_mod_exc |>  
  get_variables() |> 
  str_subset("^b_.*")

# trace
b_mod_exc |> mcmc_plot(type = "trace",
                         par = b_par_exc_mod)
 
# autocorr
b_mod_exc |> mcmc_plot(type = "acf_bar",
                         par = b_par_exc_mod)
  
# rhat
b_mod_exc |> mcmc_plot(type = "rhat_hist")

# ess
b_mod_exc |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
b_mod_exc_resids <- make_brms_dharma_res(b_mod_exc)

# qqplot
b_mod_exc_resids |> testUniformity()

#residplot
b_mod_exc_resids |> plotResiduals(quantreg = FALSE)
```

#### Save model

```{r}
save(b_mod_exc, file = "Model_Outputs/b_mod_exc.Rdata")
```

# BROWSERS

## Define formula

```{r}
b_brow_form <-
bf(browser ~ 
       Depth_m +
       Aspect_descriptive +
       Benthic_Complexity + 
       Habitat +
       (1 | Reef_2/Site),
     family = hurdle_lognormal())
```

## Data exploration

```{r}
fg_biom |> 
  group_by(Depth_m) |>
  summarise(log_median = log(median(browser)),
            log_mad = log(mad(browser))) |> 
  arrange(-log_median) |> 
  filter(log_median != "-Inf") |> 
  filter(log_mad != "-Inf")
```

## Weakly informative prior

```{r}
b_priors_brow <- prior(normal(0.5, 0.9), class = "Intercept") +
  prior(normal(0, 0.5), class = "b") +
  prior(student_t(3, 0, 0.9), class = "sigma") +
  prior(student_t(3, 0, 0.9), class = "sd") +
  prior(beta(1, 1), class = "hu")
```

## Prior model

```{r}
b_prior_mod_brow <- brm(b_brow_form,
                    data = fg_biom,
                    prior = b_priors_brow,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## Prior evaluation

```{r}
b_prior_mod_brow |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

# Fit model

```{r}
#| cache: true
b_mod_brow <- update(b_prior_mod_brow,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## Traceplots

```{r}
# prep
b_par_brow_mod <- b_mod_brow  |>  
  get_variables() |> 
  str_subset("^b_.*")

# trace
b_mod_brow |> mcmc_plot(type = "trace",
                         par = b_par_brow_mod)
 
# autocorr
b_mod_brow |> mcmc_plot(type = "acf_bar",
                         par = b_par_brow_mod)
  
# rhat
b_mod_brow |> mcmc_plot(type = "rhat_hist")

# ess
b_mod_brow |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
b_mod_brow_resids <- make_brms_dharma_res(b_mod_brow)

# qqplot
b_mod_brow_resids |> testUniformity()

#residplot
b_mod_brow_resids |> plotResiduals(quantreg = FALSE)
```

#### Save model

```{r}
save(b_mod_brow, file = "Model_Outputs/b_mod_brow.Rdata")
```
