---
title: "Biomass_fit"
format: html
editor: visual
---

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
#library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
#source("helperFunctions.R")
library(ggimage)
library(vegan)
library(BiodiversityR)
library(ggrepel)
```

# Read data

```{r}
fg_biom <- read_csv("Data/herb_biomass.csv",
                      trim_ws = TRUE)
glimpse(fg_biom)
```

# Declare factors

```{r}
fg_biom <- fg_biom |> 
  mutate(Site = factor(Site),
         Aspect_descriptive = factor(Aspect_descriptive),
         Habitat = factor(Habitat),
         herbs = cropper + browser + detritivore + excavator + scraper) # all herbivore column
```

# ALL HERBIVORES

# Model 1: Gaussian distribution

## define formula

```{r}
b_herbs_form <- 
  bf(herbs ~ Depth_m +
       Aspect_descriptive +
       (1 | Site) + 
       (1 | Habitat),
     family = gaussian())
```

## get prior

```{r}
get_prior(b_herbs_form, data = fg_biom)
```


## Data exploration 

```{r}
fg_biom |> 
  group_by(Depth_m,
           Aspect_descriptive) |>
  summarise(median = median(herbs),
            mad = mad(herbs)) |> 
  arrange(-median)
```

## Weakly informative priors

```{r}
b_priors_herbs <- prior(normal(15.5, 21), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(student_t(3, 0, 21), class = "sigma") +
  prior(student_t(3, 0, 21), class = "sd")
```

## Prior only model (5000 iter)

```{r}
b_prior_mod_herbs <- brm(b_herbs_form,
                    data = fg_biom,
                    prior = b_priors_herbs,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```
## Prior evaluation

```{r}
b_prior_mod_herbs |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots()
```

# Fit model (10000 iter)

```{r}
#| cache: true
b_mod_herbs <- update(b_prior_mod_herbs,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

# Residuals

```{r}
# estimate resids
b_herbs_resids <- make_brms_dharma_res(b_mod_herbs)

# test qqplot/residual
b_herbs_resids |> testUniformity() 
b_herbs_resids |> plotResiduals() 
```

# Conclusion: Gaussian model not good

# Hurdle lognormal (hurdle is used to account for zero values)

## define formula

```{r}
b_herbs_form_2 <- 
  bf(herbs ~ Depth_m +
       Aspect_descriptive +
       (1 | Site) + 
       (1 | Habitat),
     family = hurdle_lognormal())
```

## examine priors needed

```{r}
get_prior(b_herbs_form_2, data = fg_biom)
```

## Data exploration 

```{r}
fg_biom |> 
  group_by(Depth_m,
           Aspect_descriptive) |>
  summarise(log_median = log(median(herbs)),
            log_mad = log(mad(herbs))) |> 
  arrange(-log_median)
```

```{r}
1/1.15
```

## Weakly informative priors

```{r}
b_priors_herbs_2 <- prior(normal(1, 1.1), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(student_t(3, 0, 1.1), class = "sigma") +
  prior(student_t(3, 0, 1.1), class = "sd") +
  prior(beta(1, 1), class = "hu")
```

## Prior only model (5000 iter)

```{r}
b_prior_mod_herbs_2 <- brm(b_herbs_form_2,
                    data = fg_biom,
                    prior = b_priors_herbs_2,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

# Fit model

```{r}
#| cache: true
b_mod_herbs_2 <- update(b_prior_mod_herbs_2,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

# Residuals

```{r}
# estimate resids
b_herbs_resids_2 <- make_brms_dharma_res(b_mod_herbs_2)

# test qqplot/residual
b_herbs_resids_2  |> testUniformity() 
b_herbs_resids_2  |> plotResiduals() # both dont look good
```

# Hurdle lognormal looks good