---
title: "Herb_Assem_Multivariate"
format: html
editor: visual
---

# Cleanup

```{r}
rm(list=ls())
gc()
```

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(patchwork)
library(vegan)
library(BiodiversityR)
library(ggrepel)
library(ggforce)
```

# Read data

```{r}
abun_ord <- read_csv("Data/herb_assem.csv", 
                     trim_ws = TRUE)

#glimpse(abun_ord)
```

## Separate env and species matrix

```{r}
abun_env <- abun_ord |> 
  select(...1:Benthic_Complexity) |> 
  mutate(Habitat = factor(Habitat),
         Benthic_Complexity = factor(Benthic_Complexity)) |> 
  mutate(Depth_group = factor(Depth_group),
         Slope_group = factor(Slope_group)) |> 
  mutate(Depth_group = recode(Depth_group,
                              Shallow = "Shallow",
                              Upper_mesophotic = "Upper mesophotic",
                              Lower_mesophotic = "Lower mesophotic"))

abun_spmatrix <- abun_ord |> 
  select(Acanthurus_auranticavus:Zebrasoma_velifer)
```

## Wisconsin and fourth root standardization

```{r}
abun_stand <- wisconsin(abun_spmatrix^0.25)
```

# Run CAP

```{r}
#| cache: true

abun_cap <- capscale(abun_stand ~ 
                       Depth_group +
                       Slope_group +
                       Habitat + 
                       Benthic_Complexity,
                     data = abun_env,
                     distance = "bray",
                     sqrt.dist = FALSE)
```

## Plot ordination

```{r}
plot_cap <- abun_cap |> ordiplot(choices=c(1,2))
```

## Calculate abundance per site/row to scale size of dots to abundance

```{r}
abun_spmatrix_v2 <- rowSums(abun_spmatrix)

abun_env <- cbind(abun_env, # combine with env db
                  abun_spmatrix_v2) 
```

### Extract CAP scores

```{r}
scores <- sites.long(plot_cap,
                     env.data = abun_env)
```

### Plot ordination

```{r}
p_ord1 <- 
ggplot() +
  geom_point(data = scores, 
             aes(x = axis1,
                 y = axis2,
             color = Depth_group,
             size = abun_spmatrix_v2)) +
  scale_color_manual(values = c("Shallow" = "#8AA17D",
                                "Upper mesophotic" = "#929FBD",
                                "Lower mesophotic" = "#E29297")) +
  geom_hline(yintercept = 0,
             linetype = "dashed") +
  geom_vline(xintercept = 0,
             linetype = "dashed") +
  theme_classic()
```

#### Adding layers to the ordination

```{r fig.height=5, fig.width=8, dpi=300}
p_ord2 <- 
p_ord1 +
  scale_fill_discrete(breaks = c("Shallow",
                                 "Upper mesophotic",
                                 "Lower mesophotic")) +
  guides(size = "none",
         color = "none", 
         fill = guide_legend("Depth group")) +
  geom_mark_hull(data = scores,
                 aes(x = axis1,
                     y = axis2,
                     fill = Depth_group),
                 concavity = 20,
                 expand = 0) +
  scale_x_continuous(name = "CAP: 32.0% fitted, 4.1% total ") +
  scale_y_continuous(name = "CAP: 22.9% fitted, 7.0% total") +
  scale_color_manual(values = c("Shallow" = "#8AA17D",
                                "Upper mesophotic" = "#929FBD",
                                "Lower mesophotic" = "#E29297"))
```

#### Add species loadings with significance via envfit

```{r}
spec_envfit <- envfit(plot_cap, # run envfit
                      env = abun_stand,
                      permutations = 10000)

envfit_r_p <- data.frame(r = spec_envfit$vectors$r, # extract r and p values
                         p = spec_envfit$vectors$pvals)

sp_long2 <- species.long(plot_cap, # matrix for ordination scores and r and p values
             spec.data = envfit_r_p)

sp_long3 <- sp_long2 |> # extract r < 0.001 
  filter(r > 0.10)

sp_long4 <- 
  sp_long3 |> 
  mutate(labels = recode(labels,
                          "Acanthurus_pyroferus" = "Acanthurus pyroferus",
                           "Centropyge_bispinosa" = "Centropyge bispinosa",
                           "Centropyge_heraldi" = "Centropyge heraldi",
                            "Naso_tonganus" = "Naso tonganus"))
```

# Add envfit arrows unto ordination

## Plot envfit on the figures

```{r}
p_ord3 <- 
  p_ord2 + 
  geom_segment(data = sp_long4,
               aes(x = 0,
                   y = 0,
                   xend = axis1,
                   yend = axis2,
                   color = "black",
                   size = 0.5)) +
  geom_text_repel(data = sp_long4,
                  aes(x = axis1,
                      y = axis2,
                      label = labels,
                      size = 200),
                  max.overlaps = 30,
                  fontface="italic") +
  theme(axis.title=element_text(size = 15),
        axis.text=element_text(size = 12),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 18)) #+
   #scale_color_manual(values = c("Shallow" = "#8AA17D",
    #                            "Upper_meso" = "#929FBD",
     #                           "Lower_meso" = "#E29297"))
```

###Summary

```{r}
summary(abun_cap)
```

## Plot slope for ESM

```{r}
p_slope <- 
ggplot() +
  geom_point(data = scores, 
             aes(x = axis1,
                 y = axis2,
             color = Slope_group,
             size = abun_spmatrix_v2)) +
  scale_color_manual(values = c("Flat" = "#8AA17D",
                                "Slope" = "#929FBD",
                                "Wall" = "#E29297")) +
  geom_hline(yintercept = 0,
             linetype = "dashed") +
  geom_vline(xintercept = 0,
             linetype = "dashed") +
  scale_fill_discrete(breaks = c("Flat",
                                 "Slope",
                                 "Wall")) +
  guides(size = "none",
         color = guide_legend("Slope group"), 
         fill = guide_legend("Slope group")) +
  geom_mark_hull(data = scores,
                 aes(x = axis1,
                     y = axis2,
                     fill = Slope_group),
                 concavity = 20,
                 expand = 0) +
  scale_x_continuous(name = "CAP: 32.0% fitted, 4.1% total") +
  scale_y_continuous(name = "CAP: 22.9% fitted, 7.0% total") +
  theme_classic() +
  theme(axis.title=element_text(size = 15),
        axis.text=element_text(size = 12),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 18))
```

## Plot zone for ESM

```{r}
p_zone <- 
ggplot() +
  geom_point(data = dplyr::filter(scores, Habitat != "passage"), 
             aes(x = axis1,
                 y = axis2,
             color = Habitat,
             size = abun_spmatrix_v2)) +
  scale_color_manual(values = c("Inner reef" = "#8AA17D",
                                "Lagoon" = "#929FBD",
                                "Outer reef" = "#E29297")) +
  geom_hline(yintercept = 0,
             linetype = "dashed") +
  geom_vline(xintercept = 0,
             linetype = "dashed") +
  scale_fill_discrete(breaks = c("Inner reef",
                                 "Lagoon",
                                 "Outer reef")) +
  guides(size = "none",
         color = "none", 
         fill = guide_legend("Habitat")) +
  geom_mark_hull(data = scores,
                 aes(x = axis1,
                     y = axis2,
                     fill = Habitat),
                 concavity = 20,
                 expand = 0) +
  scale_x_continuous(name = "CAP: 32.0% fitted, 4.1% total") +
  scale_y_continuous(name = "CAP: 22.9% fitted, 7.0% total") +
  theme_classic() +
  theme(axis.title=element_text(size = 15),
        axis.text=element_text(size = 12),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 18))
```

### Combine plots

```{r}
p_zone_slope <- 
p_zone / p_slope + 
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 15))
```

### ggsave

```{r}
ggsave("Figures/Fig. SX. assem_zone_slope.jpeg",
       plot = p_zone_slope, 
       dpi = 600, 
       height = 8, 
       width = 8, 
       units = "in")
```

# PERMANOVA

```{r}
adonis2(abun_stand ~ 
          Depth_group +
          Slope_group +
          Habitat + 
          Benthic_Complexity, 
        data = abun_env,
        perm = 10000)
```

# Plot mean +/- se

## Function for se

```{r}
se <- function(x, na.rm = TRUE) {
  x <- if (na.rm) na.omit(x) else x
  sd(x) / sqrt(length(x))
}
```

# Fig abundance

```{r}
ord_mean_abun <- 
abun_ord |> 
  select(Depth_group,
         Centropyge_bispinosa,
         Acanthurus_pyroferus,
         Naso_tonganus,
         Centropyge_heraldi) |> 
  pivot_longer(!Depth_group, 
               names_to = "Species",
               values_to = "Abundance") |> 
  mutate(Depth_group = factor(Depth_group,
         levels = c("Shallow",
                    "Upper_mesophotic",
                    "Lower_mesophotic")),
         # Replace underscores with spaces and create expressions for italics
         Species = gsub("_", " ", Species),
         Species = paste0("italic('", Species, "')")) |> 
  group_by(Depth_group, Species) |> 
  summarise(MEAN = mean(Abundance),
            STDE = se(Abundance)) |> 
  ggplot(aes(x = Depth_group,
             y = MEAN, 
             color = Depth_group)) +
  geom_pointrange(aes(ymin = MEAN - STDE,
                      ymax = MEAN + STDE)) +
  facet_wrap(
    ~ Species,
    scales = "free",
    labeller = label_parsed    # interprets the italic() expressions
  ) +
  scale_x_discrete(labels = function(x) gsub("_", " ", x)) +
  labs(x = "Depth group",
       y = expression(Abundance~(ind.~150*m^{-2}))) +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 20,
                               vjust = 0.85,
                               hjust = 0.70,
                               size = 12),
    axis.title = element_text(size = 15),
    axis.text.y = element_text(size = 12),
    legend.position = "none",
    strip.text = element_text(size = 15)
  )
```

## ggsave

```{r}
ggsave("Figures/Fig. SX. assem_abundance.jpeg",
       plot = ord_mean_abun, 
       dpi = 600, 
       height = 6, 
       width = 10, 
       units = "in")
```
