---
title: "Herb_Assem_Multivariate"
format: html
editor: visual
---

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(patchwork)
library(vegan)
library(BiodiversityR)
library(ggrepel)
library(ggforce)
```

# Read data

```{r}
abun_ord <- read_csv("Data/herb_assem.csv", 
                     trim_ws = TRUE)

glimpse(abun_ord)
```

# Separate env and species matrix

```{r}
abun_env <- abun_ord |> 
  select(...1:Aspect_descriptive)

abun_spmatrix <- abun_ord |> 
  select(Acanthurus_auranticavus:Zebrasoma_velifer)
```

# Wisconsin and fourth root standardization

```{r}
abun_stand <- wisconsin(abun_spmatrix^0.25)
```

# Run CAP

```{r}
#| cache: true

abun_cap <- capscale(abun_stand ~ Depth_group +
                       Slope_group,
                     data = abun_env,
                     distance = "bray",
                     sqrt.dist = FALSE)
```

# Plot ordination

```{r}
plot_cap <- abun_cap |> ordiplot(choices=c(1,2))
```

# Calculate abundance per site/row to scale size of dots to abundance

```{r}
abun_spmatrix_v2 <- rowSums(abun_spmatrix)

abun_env <- cbind(abun_env, # combine with env db
                  abun_spmatrix_v2) 
```

# Extract CAP scores

```{r}
scores <- sites.long(plot_cap,
                     env.data = abun_env)
```

# Plot ordination

```{r}
p_ord1 <- 
ggplot() +
  geom_point(data = scores, 
             aes(x = axis1,
                 y = axis2,
             color = Depth_group,
             size = abun_spmatrix_v2)) +
  scale_color_manual(values = c("Shallow" = "#8AA17D",
                                "Upper_mesophotic" = "#929FBD",
                                "Lower_mesophotic" = "#E29297")) +
  geom_hline(yintercept = 0,
             linetype = "dashed") +
  geom_vline(xintercept = 0,
             linetype = "dashed") +
  theme_classic()
```

# Adding layers to the ordination

```{r fig.height=5, fig.width=8, dpi=300}
p_ord2 <- 
p_ord1 +
  scale_fill_discrete(breaks = c("Shallow",
                                 "Upper_mesophotic",
                                 "Lower_mesophotic")) +
  guides(size = "none",
         color = "none", 
         fill = guide_legend("Depth_group")) +
  geom_mark_hull(data = scores,
                 aes(x = axis1,
                     y = axis2,
                     fill = Depth_group),
                 concavity = 20,
                 expand = 0) +
  scale_x_continuous(name = "CAP: 47.04% fitted, 4.5% total ") +
  scale_y_continuous(name = "CAP: 26.46% fitted, 2.5% total") +
  scale_color_manual(values = c("Shallow" = "#8AA17D",
                                "Upper_meso" = "#929FBD",
                                "Lower_meso" = "#E29297"))
```

# Add species loadings with significance via envfit

```{r}
spec_envfit <- envfit(plot_cap, # run envfit
                      env = abun_stand,
                      permutations = 10000)

envfit_r_p <- data.frame(r = spec_envfit$vectors$r, # extract r and p values
                         p = spec_envfit$vectors$pvals)

sp_long2 <- species.long(plot_cap, # matrix for ordination scores and r and p values
             spec.data = envfit_r_p)

sp_long3 <- sp_long2 |> # extract r < 0.001 
  filter(p < 0.001) 

labels_abb <- c("An", "Ap", "Cbis", "Ch", "Cbin", "Nl") #manually abbreviate cause the "_" messes with the mutate abb

sp_long4 <- cbind(sp_long3, labels_abb) # db with abbreviated labels
```

# Add envfit arrows unto ordination

## Plot envfit on the figures

```{r}
p_ord3 <- p_ord2 + 
  geom_segment(data = sp_long4,
               aes(x = 0,
                   y = 0,
                   xend = axis1,
                   yend = axis2,
                   color = "black",
                   size = 0.5)) +
  geom_text_repel(data = sp_long4,
                  aes(x = axis1,
                      y = axis2,
                      label = labels_abb,
                      size = 200),
                  max.overlaps = 30) +
  theme(axis.title=element_text(size = 15),
        axis.text=element_text(size = 12),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 18))
```

## Plot slope for ESM

```{r}
p_slope <- 
ggplot() +
  geom_point(data = scores, 
             aes(x = axis1,
                 y = axis2,
             color = Slope_group,
             size = abun_spmatrix_v2)) +
  scale_color_manual(values = c("Flat" = "#8AA17D",
                                "Slope" = "#929FBD",
                                "Wall" = "#E29297")) +
  geom_hline(yintercept = 0,
             linetype = "dashed") +
  geom_vline(xintercept = 0,
             linetype = "dashed") +
  scale_fill_discrete(breaks = c("Flat",
                                 "Slope",
                                 "Wall")) +
  guides(size = "none",
         color = "none", 
         fill = guide_legend("Slope_group")) +
  geom_mark_hull(data = scores,
                 aes(x = axis1,
                     y = axis2,
                     fill = Slope_group),
                 concavity = 20,
                 expand = 0) +
  scale_x_continuous(name = "CAP: 47.04% fitted, 4.5% total ") +
  scale_y_continuous(name = "CAP: 26.46% fitted, 2.5% total") +
  theme_classic() +
  theme(axis.title=element_text(size = 15),
        axis.text=element_text(size = 12),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 18))
```

## ggsave

```{r}
ggsave("Fig. SX. assem_slope.jpeg",
       plot = p_slope, 
       dpi = 600, 
       height = 5, 
       width = 7, 
       units = "in")
```

# PERMANOVA

```{r}
adonis2(abun_stand ~ Depth_group +
          Slope_group, 
        data = abun_env,
        perm = 10000)
```

# Fig abundance

```{r}
ord_mean_abun <- 
abun_ord |> 
  select(Depth_group,
         Naso_lituratus, 
         Acanthurus_nigricans,
         Centropyge_bispinosa,
         Acanthurus_pyroferus,
         Ctenochaetus_binotatus,
         Centropyge_heraldi) |> 
  pivot_longer(!Depth_group, 
               names_to = "Species",
               values_to = "Abundance") |> 
  mutate(Depth_group = factor(Depth_group,
         levels = c("Shallow",
                    "Upper_mesophotic",
                    "Lower_mesophotic"))) |> 
  group_by(Depth_group,
           Species) |> 
  summarise(MEAN = mean(Abundance),
            STDE = std_error(Abundance)) |> 
  ggplot(aes(x = Depth_group,
             y = MEAN, 
         color = Depth_group)) +
  geom_pointrange(aes(ymin = MEAN - STDE,
                      ymax = MEAN + STDE)) +
  facet_wrap(~ Species,
             scales = "free") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 20,
                                 vjust = 0.85,
                                 hjust = 0.70,
                                 size = 12),
        axis.title = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        legend.position = "none",
        strip.text = element_text(size = 15)) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)))
```

## ggsave

```{r}
ggsave("Fig. SX. assem_abundance.jpeg",
       plot = ord_mean_abun, 
       dpi = 600, 
       height = 6, 
       width = 10, 
       units = "in")
```