---
title: "Abundance_fit"
format: html
editor: visual
---

# Cleanup

```{r}
rm(list=ls())
gc()
```

Quarto document for fitting abundance among depth bands, reef zones and slope orientation using Bayesian and negative binomial distribution. Site nested in reef are considered group level variables.

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
#library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(vegan)
library(BiodiversityR)
library(ggrepel)
set.seed(123)
```

# Read data

```{r}
fg_abun <- 
  read_csv("Data/herb_abundance.csv",
           trim_ws = TRUE)

#glimpse(fg_abun)
```

# Declare factors

```{r}
fg_abun <- fg_abun |> 
  mutate(Reef_2 = factor(Reef_2),
         Site = factor(Site),
         Aspect_descriptive = factor(Aspect_descriptive),
         Benthic_Complexity = factor(Benthic_Complexity),
         Habitat = factor(Habitat),
         herbs = cropper + browser + detritivore + excavator + scraper) # all herbivore column
```

# ALL HERBIVORES

## Define formula

```{r}
herbs_form <- 
  bf(herbs ~ 
       Depth_m +
       Aspect_descriptive +
       Benthic_Complexity + 
       Habitat +
       (1 | Reef_2/Site),
     family = negbinomial(link = "log"))
```

## Data exploration

```{r}
fg_abun |> 
  summarise(log_med = log(median(herbs)),
            log_mad = log(mad(herbs))) 
```

## Weakly informative priors

```{r}
herb_priors <- prior(normal(1.2, 2), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 2), class = "sd")
```

## Herbs prior only

```{r}
#| cache: true
herbs_prior_mod <- brm(herbs_form,
                    data = fg_abun,
                    prior = herb_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    seed = 123,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

### Prior evaluation

```{r}
herbs_prior_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

# Fit model

```{r}
#| cache: true
herbs_mod <- update(herbs_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

### Partial plot

```{r}
herbs_mod |> 
  conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots()
```

### Trace plots

```{r}
par_herbs <- herbs_mod |>  
  get_variables() |> 
  str_subset("^b_.*")

# trace
herbs_mod |> mcmc_plot(type = "trace",
                         par = par_herbs)
# autocorr
herbs_mod |> mcmc_plot(type = "acf_bar",
                         par = par_herbs)

# rhat
herbs_mod |> mcmc_plot(type = "rhat_hist")

# ess
herbs_mod |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
herbs_resids <- make_brms_dharma_res(herbs_mod)

# qqplot
herbs_resids |> testUniformity()

# residplot
herbs_resids |> plotResiduals()

# testdisp
herbs_resids |> testDispersion()
```

#### Save model

```{r}
save(herbs_mod, file = "Model_Outputs/herbs_mod.Rdata")
```

# CROPPERS

## Define formula

```{r}
crop_formula <- 
  bf(cropper ~ 
       Depth_m +
       Aspect_descriptive +
       Benthic_Complexity + 
       Habitat +
       (1 | Reef_2/Site),
     family = negbinomial(link = "log"))
```

## Data exploration

```{r}
fg_abun |> 
  summarise(log_med = log(median(cropper)),
            log_mad = log(mad(cropper)))
```

## Weakly informative priors

```{r}
priors_crop <- prior(normal(0.5, 2), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 2), class = "sd")
```

## Crops prior only

```{r}
#| cache: true
crop_prior_mod <- brm(crop_formula,
                    data = fg_abun,
                    prior = priors_crop,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    seed = 123,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## Prior evaluation

```{r}
crop_prior_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

# Fit model

```{r}
#| cache: true
crop_mod <- update(crop_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

### Trace plots

```{r}
# subset
par_crop <- crop_mod |>  
  get_variables() |> 
  str_subset("^b_.*")

# trace
crop_mod |> mcmc_plot(type = "trace",
                         par = par_crop)
# autocorr
crop_mod  |> mcmc_plot(type = "acf_bar",
                         par = par_crop)
# rhat
crop_mod |> mcmc_plot(type = "rhat_hist")
# ess
crop_mod|> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
crop_resids <- make_brms_dharma_res(crop_mod)
# qqplot
crop_resids |> testUniformity()
# residplot
crop_resids |> plotResiduals()
# testdisp
crop_resids |> testDispersion()
```

#### Save model

```{r}
save(crop_mod, file = "Model_Outputs/crop_mod.Rdata")
```

# DETRITIVORES

## Define formula

```{r}
det_form <- 
  bf(detritivore ~ 
       Depth_m +
       Aspect_descriptive +
       Benthic_Complexity + 
       Habitat +
       (1 | Reef_2/Site),
     family = negbinomial(link = "log"))
```

## Prior exploration

```{r}
fg_abun |> 
  group_by(Depth_m,
           Aspect_descriptive) |>
  summarise(med = log(median(detritivore)),
            mad = log(mad(detritivore)))
```

## Weakly informative priors

```{r}
det_priors <- prior(normal(0.5, 0.8), class = "Intercept") +
  prior(normal(0, 2.2), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0 , 0.8), class = "sd")
```

## Dets prior only

```{r}
#| cache: true
det_prior_mod <- brm(det_form,
                    data = fg_abun ,
                    prior = det_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    seed = 123,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 1000)
```

## Eval prior model

```{r}
det_prior_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

# Fit model

```{r}
#| cache: true
det_mod <- update(det_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

### Partial plot

```{r}
det_mod |> 
  conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots()
```

### Trace plot

```{r}
# subset
par_det <- det_mod |>  
  get_variables() |> 
  str_subset("^b_.*")

# trace
det_mod |> mcmc_plot(type = "trace",
                         par = par_det)
# autocorr
det_mod  |> mcmc_plot(type = "acf_bar",
                         par = par_det)
# rhat
det_mod |> mcmc_plot(type = "rhat_hist")
# ess
det_mod  |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
det_resids <- make_brms_dharma_res(det_mod)
# qqplot
det_resids |> testUniformity()
# residplot
det_resids |> plotResiduals()
# testdisp
det_resids |> testDispersion()
```

#### Save model

```{r}
save(det_mod, file = "Model_Outputs/det_mod.Rdata")
```

# SCRAPERS

## Define formula

```{r}
scra_form <- 
  bf(scraper ~ 
        Depth_m +
       Aspect_descriptive +
       Benthic_Complexity + 
       Habitat +
       (1 | Reef_2/Site),
     family = negbinomial(link = "log"))
```

## Explore priors

```{r}
fg_abun |> 
  group_by(Depth_m,
           Aspect_descriptive) |>
  summarise(med = log(median(scraper)),
            mad = log(mad(scraper)))
```

## Weakly informative priors

```{r}
scra_priors <- prior(normal(2, 1), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1), class = "sd")
```

## Scra prior only

```{r}
#| cache: true
scra_prior_mod <- brm(scra_form,
                    data = fg_abun,
                    prior = scra_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    seed = 123,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## Eval prior only

```{r}
scra_prior_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

# Fit model

```{r}
#| cache: true
scra_mod <- update(scra_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

### Partial plots

```{r}
scra_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots()
```

### Trace plots

```{r}
par_scra <- scra_mod |>  
  get_variables() |> 
  str_subset("^b_.*")
# trace
scra_mod |> mcmc_plot(type = "trace",
                         par = par_scra)
# autocorr
scra_mod |> mcmc_plot(type = "acf_bar",
                         par = par_scra)
# rhat
scra_mod |> mcmc_plot(type = "rhat_hist")
# ess
scra_mod |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
scra_resids <- make_brms_dharma_res(scra_mod)
# qqplot
scra_resids |> testUniformity()
# residplot
scra_resids |> plotResiduals()
# testdisp
scra_resids |> testDispersion()
```

#### Save model

```{r}
save(scra_mod, file = "Model_Outputs/scra_mod.Rdata")
```

# EXCAVATORS

## Define formula

```{r}
exc_form <- 
  bf(excavator ~ 
       Depth_m +
       Aspect_descriptive +
       Benthic_Complexity + 
       Habitat +
       (1 | Reef_2/Site),
     family = negbinomial(link = "log"))
```

## Prior exploration

```{r}
fg_abun |> 
  group_by(Depth_m,
           Aspect_descriptive) |>
  summarise(med = log(median(excavator)),
            mad = log(mad(excavator)))
```

## Weakly informative priors

```{r}
exc_priors <- prior(normal(2.3, 2.7), class = "Intercept") +
  prior(normal(0, 0.2), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 2.7), class = "sd")
```

## Exc prior model

```{r}
#| cache: true
exc_prior_mod <- brm(exc_form,
                    data = fg_abun,
                    prior = exc_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    seed = 123,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## Eval priors

```{r}
exc_prior_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

# Fit model

```{r}
#| cache: true
exc_mod <- update(exc_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

### Partial plots

```{r}
exc_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots()
```

### Trace plots

```{r}
par_exc <- exc_mod |>  
  get_variables() |> 
  str_subset("^b_.*")
# trace
exc_mod  |> mcmc_plot(type = "trace",
                         par = par_exc)
# autocorr
exc_mod |> mcmc_plot(type = "acf_bar",
                         par = par_exc)
# rhat
exc_mod|> mcmc_plot(type = "rhat_hist")
# ess
exc_mod |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
exc_resids <- make_brms_dharma_res(exc_mod) 
# qqplot
exc_resids |> testUniformity()
# residplot
exc_resids |> plotResiduals()
# testdisp
exc_resids |> testDispersion()
```

#### Save model

```{r}
save(exc_mod, file = "Model_Outputs/exc_mod.Rdata")
```

# BROWSER

## Define formula

```{r}
brow_form <- 
  bf(browser ~
       Depth_m +
       Aspect_descriptive +
       Benthic_Complexity + 
       Habitat +
       (1 | Reef_2/Site),
     family = negbinomial(link = "log"))
```

## Prior exploration

```{r}
fg_abun |> 
  group_by(Depth_m,
           Aspect_descriptive) |>
  summarise(med = log(median(browser)),
            mad = log(mad(browser)))
```

## Define prior

```{r}
brow_prior <- prior(normal(0.5, 1), class = "Intercept") +
  prior(normal(0, 3), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1), class = "sd")
```

## Brow prior model

```{r}
#| cache: true

brow_mod_prior <- brm(brow_form,
                    data = fg_abun,
                    prior = brow_prior,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    seed = 123,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## Evaluate priors

```{r}
brow_mod_prior  |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

# Fit model

```{r}
#| cache: true
brow_mod <- update(brow_mod_prior,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

### Traceplot

```{r}
par_brow <- brow_mod |>  
  get_variables() |> 
  str_subset("^b_.*")
# trace
brow_mod |> mcmc_plot(type = "trace",
                         par = par_brow)
# autocorr
brow_mod |> mcmc_plot(type = "acf_bar",
                         par = par_brow)
# rhat
brow_mod |> mcmc_plot(type = "rhat_hist")
# ess
brow_mod |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
brow_resids <- make_brms_dharma_res(brow_mod)
# qqplot
brow_resids |> testUniformity()
# residplot
brow_resids |> plotResiduals()
# testdisp
brow_resids |> testDispersion()
```

#### Save model

```{r}
save(brow_mod, file = "Model_Outputs/brow_mod.Rdata")
```
