---
title: "abun_results_plots"
format: html
editor: visual
---

Quarto document for interpreting and plotting abundance among depth bands and slope orientation.

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
#library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
#source("helperFunctions.R")
library(ggimage)
library(vegan)
library(BiodiversityR)
library(ggrepel)
```


#  HERBIVORES

## exceedence probability

```{r}
herbs_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> 
  summarise_draws(median,
                  HDInterval::hdi, # logscale so exponentiate
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 | 
           Pg > 0.85)
```

## dpeth

## newdata herbs

```{r}
depth_newdata <- with(fg_abun,
                 data.frame(Depth_m = seq(min(Depth_m),
                                          max(Depth_m),
                                          length = 100)))
```

## predict herbs

```{r}
herbs_depth_pred <- herbs_mod |> 
  emmeans(~ Depth_m, 
          at = depth_newdata, 
          type = "response") |> 
  as.data.frame()
```

## herbs depth plot

```{r}
p_depth_allherbs_A <-
herbs_depth_pred |> 
  ggplot(aes(y = prob,
             x = Depth_m)) +
    geom_point(data = fg_abun,
             aes(y = herbs),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 60),
  breaks = seq(0, 60, by = 20)) +
  scale_x_continuous(name = "",
                     breaks = seq(0, 100, by = 20)) +
geom_image(data = tibble(Depth_m = 90,
                            prob = 57),
                            aes(image = ("naso.png")),
                            size = 0.30) +
  geom_image(data = tibble(Depth_m = 90,
                            prob = 47),
                            aes(image = ("ctenochaetus.png")),
                            size = 0.30) +
  geom_image(data = tibble(Depth_m = 70,
                            prob = 57),
                            aes(image = ("scarus.png")),
                            size = 0.30) +
    geom_image(data = tibble(Depth_m = 70,
                            prob = 47),
                            aes(image = ("chlorurus.png")),
                            size = 0.30) +
  ggtitle("Total herbivores") +
  theme_classic() +
     theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18)) + 
  theme(legend.position = "none") 
```

## slope

## herbs slope newdata

```{r}
herbs_nd_slope <- emmeans(herbs_mod,
                          ~Aspect_descriptive,
                          type = "response") |> 
  as.data.frame()
```

## herbs slope plot

```{r}
p_slope_allherbs_A <- 
herbs_nd_slope |> 
  ggplot(aes(x = Aspect_descriptive,
             y = prob)) +
  geom_pointrange(aes(ymin = lower.HPD,
                      ymax = upper.HPD),
                  shape = 21,
                  size = 1,
                  fatten = 3,
                  color = "#8AA17D",
                  fill = "#8AA17D") +
  scale_y_continuous(Abundance~(ind.150m^-2),
                     limits = c(0, 15),
                     breaks = seq(0, 15, by = 5)) +
  scale_x_discrete(name = "") +
  theme_classic() +
  ggtitle("Total herbivores") +
     theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 15),
        plot.title = element_text(size = 18)) +
    geom_image(data = tibble(Aspect_descriptive = 5,
                           prob = 14),
             aes(image = "naso.png"),
             size = 0.30) +
    geom_image(data = tibble(Aspect_descriptive = 5,
                           prob = 11),
             aes(image = "ctenochaetus.png"),
             size = 0.30) +
      geom_image(data = tibble(Aspect_descriptive = 4,
                           prob = 14),
             aes(image = "scarus.png"),
             size = 0.30) +
    geom_image(data = tibble(Aspect_descriptive = 4,
                           prob = 11),
             aes(image = "chlorurus.png"),
             size = 0.30)
```

## pairwise for herbs slope

```{r}
herbs_mod |> emmeans(~ Aspect_descriptive,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  mutate(Exp = exp(.value)) |> 
  dplyr::select(-.chain, 
                -.value,
                -.iteration) |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  Pl = ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  dplyr::filter(Pl > 0.85 | 
           Pg > 0.85)
```

## plot slope contrasts

```{r}
abun_slope_pair <-herbs_mod |> emmeans(~ Aspect_descriptive,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  summarise(median_hdci(exp(.value),
                        .width = c(0.85, 0.95))) 
  
 p_abun_slope_pair <- ggplot() + 
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = abun_slope_pair |> filter(.width == 0.85),
                  linewidth = 1.7) +
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = abun_slope_pair |> filter(.width == 0.95),
                  pch = 21,
                  size = 1.2,
                  fill = "#8AA17D",
                  linewidth = 0.7) +
  geom_hline(yintercept = 1, 
             linetype = "dashed",
             color = "red",
             linewidth = 1) +
    coord_flip() +
  theme_classic() +
  scale_x_discrete(name = "Constrast: slope orientation") +
  scale_y_continuous(name = "Scaled effect size",
                   trans = scales::log2_trans()) +
  ggtitle("Abundance") +
  theme(axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        plot.title = element_text(size = 18))
```
# BROWSERS

## exceedence probability

```{r}
brow_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))|> 
  filter(Pl > 0.85 | 
           Pg > 0.85)
```

## brow predict

```{r}
brow_depth_pred <- brow_mod |> 
  emmeans(~ Depth_m, 
          at = depth_newdata, 
          type = "response") |> 
  as.data.frame()
```

## brow depth plot

```{r}
p_depth_brow_A <- 
brow_depth_pred |> 
  ggplot(aes(y = prob,
             x = Depth_m)) +
    geom_point(data = fg_abun,
             aes(y = browser),
             size = 2.5,
             shape = 21,
             color = "#929FBD",
             fill = "#929FBD",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#929FBD") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#929FBD",
              color = "#929FBD",
              alpha = 0.6) +
  scale_y_continuous(name = "",
                       limits = c(0, 60),
    breaks = seq(0, 60, by = 20)) +
  scale_x_continuous(name = "",
                     breaks = seq(0, 100, by = 20)) +
  theme_classic() +
  ggtitle("Browsers") +
   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_text(size = 18)) +
  geom_image(data = tibble(Depth_m = 90,
                           prob = 57),
             aes(image = "naso.png"),
             size = 0.30)
```

## slope

### brow slope newdata

```{r}
brow_nd_slope <- emmeans(brow_mod,
                          ~Aspect_descriptive,
                          type = "response") |> 
  as.data.frame()
```

### brow slope plot

```{r}
p_slope_brow_A <- 
brow_nd_slope |> 
  ggplot(aes(x = Aspect_descriptive,
             y = prob)) +
  geom_pointrange(aes(ymin = lower.HPD,
                      ymax = upper.HPD),
                  shape = 21,
                  size = 1,
                  fatten = 3,
                  color = "#929FBD",
                  fill = "#929FBD") +
  scale_y_continuous(name = "",
                     limits = c(0, 5),
                     breaks = seq(0, 5, by = 2.5)) +
  scale_x_discrete(name = "") +
  theme_classic() +
  ggtitle("Browsers") +
     theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 15),
        plot.title = element_text(size = 18)) +
  geom_image(data = tibble(Aspect_descriptive = 5,
                           prob = 4.7),
             aes(image = "naso.png"),
             size = 0.30)
```

## slope pairwise

```{r}
brow_mod|> emmeans(~ Aspect_descriptive,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  mutate(Exp = exp(.value)) |> 
  dplyr::select(-.chain, 
                -.value,
                -.iteration) |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  Pl = ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  dplyr::filter(Pl > 0.85 | 
           Pg > 0.85)
```

## plot pairwise

```{r}
brow_abun_slope_pair <- brow_mod |> emmeans(~ Aspect_descriptive,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  summarise(median_hdci(exp(.value),
                        .width = c(0.85, 0.95))) 
  
 p_brow_abun_slope_pair <- ggplot() + 
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = brow_abun_slope_pair|> filter(.width == 0.85),
                  linewidth = 1.7) +
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = brow_abun_slope_pair|> filter(.width == 0.95),
                  pch = 21,
                  size = 1.2,
                  fill = "#929FBD",
                  linewidth = 0.7) +
  geom_hline(yintercept = 1, 
             linetype = "dashed",
             color = "red",
             linewidth = 1) +
    coord_flip() +
  theme_classic() +
  scale_x_discrete(name = "Constrast: slope orientation") +
  scale_y_continuous(name = "",
                   trans = scales::log2_trans()) +
  ggtitle("Browsers") +
  theme(axis.title = element_text(size = 15),
        axis.text = element_text(size = 12),
        plot.title = element_text(size = 18))
```


# CROPPERS

## exceedence probability

```{r}
crop_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))|> 
  filter(Pl > 0.85 | 
           Pg > 0.85)
```

## crop predict

```{r}
crop_depth_pred <- crop_mod |> 
  emmeans(~ Depth_m, 
          at = depth_newdata, 
          type = "response") |> 
  as.data.frame()
```

## crop depth plot

```{r}
p_depth_crop_A <- 
crop_depth_pred |> 
  ggplot(aes(y = prob,
             x = Depth_m)) +
    geom_point(data = fg_abun,
             aes(y = cropper),
             size = 2.5,
             shape = 21,
             color = "#DDD487",
             fill = "#DDD487",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#DDD487") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#DDD487",
              color = "#DDD487",
              alpha = 0.6) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 60),
    breaks = seq(0, 60, by = 20)) +
  scale_x_continuous(name = "",
                     breaks = seq(0, 100, by = 20)) +
  theme_classic() +
  ggtitle("Croppers") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18)) +
  geom_image(data = tibble(Depth_m = 90,
                           prob = 57),
             aes(image = "siganid.png"),
             size = 0.30)
```

## slope

## crop slope newdata

```{r}
crop_nd_slope <- emmeans(crop_mod,
                          ~Aspect_descriptive,
                          type = "response") |> 
  as.data.frame()
```

## crop slope plot

```{r}
p_slope_crop_A <- 
crop_nd_slope |> 
  ggplot(aes(x = Aspect_descriptive,
             y = prob)) +
  geom_pointrange(aes(ymin = lower.HPD,
                      ymax = upper.HPD),
                  shape = 21,
                  size = 1,
                  fatten = 3,
                  color = "#DDD487",
                  fill = "#DDD487") +
  scale_y_continuous(Abundance~(ind.150m^-2),
                     limits = c(0, 10),
                     breaks = seq(0, 10, by = 5)) +
  scale_x_discrete(name = "") +
  theme_classic() +
  ggtitle("Croppers") + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 15),
        plot.title = element_text(size = 18)) +
  geom_image(data = tibble(Aspect_descriptive = 5,
                           prob = 9.7),
             aes(image = "siganid.png"),
             size = 0.30)
```

## slope pairwise

```{r}
crop_mod|> emmeans(~ Aspect_descriptive,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  mutate(Exp = exp(.value)) |> 
  dplyr::select(-.chain, 
                -.value,
                -.iteration) |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  Pl = ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  dplyr::filter(Pl > 0.85 | 
           Pg > 0.85)
```

## plot pairwise

```{r}
crop_abun_slope_pair <- crop_mod |> emmeans(~ Aspect_descriptive,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  summarise(median_hdci(exp(.value),
                        .width = c(0.85, 0.95))) 
  
 p_crop_abun_slope_pair <- ggplot() + 
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = crop_abun_slope_pair|> filter(.width == 0.85),
                  linewidth = 1.7) +
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = crop_abun_slope_pair|> filter(.width == 0.95),
                  pch = 21,
                  size = 1.2,
                  fill = "#DDD487",
                  linewidth = 0.7) +
  geom_hline(yintercept = 1, 
             linetype = "dashed",
             color = "red",
             linewidth = 1) +
    coord_flip() +
  theme_classic() +
  scale_x_discrete(name = "") +
  scale_y_continuous(name = "",
                   trans = scales::log2_trans()) +
  ggtitle("Croppers") +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# DETRITIVORES

## exceedence probability

```{r}
det_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))|> 
  filter(Pl > 0.85 | 
           Pg > 0.85)
```

##     det predict

```{r}
det_depth_pred <- det_mod |> 
  emmeans(~ Depth_m, 
          at = depth_newdata, 
          type = "response") |> 
  as.data.frame()
```

## det depth plot

```{r}
p_depth_det_A <- 
det_depth_pred |> 
  ggplot(aes(y = prob,
             x = Depth_m)) +
    geom_point(data = fg_abun,
             aes(y = detritivore),
             size = 2.5,
             shape = 21,
             color = "#BFB59E",
             fill = "#BFB59E",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#BFB59E") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#BFB59E",
              color = "#BFB59E",
              alpha = 0.6) +
  scale_y_continuous(name = "",
                       limits = c(0, 60),
    breaks = seq(0, 60, by = 20)) +
  scale_x_continuous(name = "",
                     breaks = seq(0, 100, by = 20)) +
  theme_classic() +
  ggtitle("Detritivores") +
   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_text(size = 18)) +
  geom_image(data = tibble(Depth_m = 90,
                           prob = 57),
             aes(image = "ctenochaetus.png"),
             size = 0.30)
```

## slope

### det slope newdata

```{r}
det_nd_slope <- emmeans(det_mod,
                          ~Aspect_descriptive,
                          type = "response") |> 
  as.data.frame()
```

### det slope plot

```{r}
p_slope_det_A <- 
det_nd_slope |> 
  ggplot(aes(x = Aspect_descriptive,
             y = prob)) +
  geom_pointrange(aes(ymin = lower.HPD,
                      ymax = upper.HPD),
                  shape = 21,
                  size = 1,
                  fatten = 3,
                  color = "#BFB59E",
                  fill = "#BFB59E") +
  scale_y_continuous(name = "",
                     limits = c(0, 5),
                     breaks = seq(0, 5, by = 2.5)) +
  scale_x_discrete(name = "") +
  theme_classic() +
  ggtitle("Detritivores") +
      theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 15),
        plot.title = element_text(size = 18)) +
  geom_image(data = tibble(Aspect_descriptive = 5,
                           prob = 4.8),
             aes(image = "ctenochaetus.png"),
             size = 0.30)
```

## slope pairwise

```{r}
det_mod|> emmeans(~ Aspect_descriptive,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  mutate(Exp = exp(.value)) |> 
  dplyr::select(-.chain, 
                -.value,
                -.iteration) |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  Pl = ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  dplyr::filter(Pl > 0.85 | 
           Pg > 0.85)
```

## plot pairwise

```{r}
det_abun_slope_pair <- det_mod |> emmeans(~ Aspect_descriptive,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  summarise(median_hdci(exp(.value),
                        .width = c(0.85, 0.95))) 
  
 p_det_abun_slope_pair <- ggplot() + 
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = det_abun_slope_pair|> filter(.width == 0.85),
                  linewidth = 1.7) +
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = det_abun_slope_pair|> filter(.width == 0.95),
                  pch = 21,
                  size = 1.2,
                  fill = "#BFB59E",
                  linewidth = 0.7) +
  geom_hline(yintercept = 1, 
             linetype = "dashed",
             color = "red",
             linewidth = 1) +
    coord_flip() +
  theme_classic() +
  scale_x_discrete(name = "") +
  scale_y_continuous(name = "",
                   trans = scales::log2_trans()) +
  ggtitle("Detritivores") +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# EXCAVATORS

## exceedence probability

```{r}
exc_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))|> 
  filter(Pl > 0.85 | 
           Pg > 0.85)
```

## exc predict

```{r}
exc_depth_pred <- exc_mod |> 
  emmeans(~ Depth_m, 
          at = depth_newdata, 
          type = "response") |> 
  as.data.frame()
```

## exc depth plot

```{r}
p_depth_exc_A <- 
exc_depth_pred |> 
  ggplot(aes(y = prob,
             x = Depth_m)) +
    geom_point(data = fg_abun,
             aes(y = excavator),
             size = 2.5,
             shape = 21,
             color = "#E29297",
             fill = "#E29297",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#E29297") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#E29297",
              color = "#E29297",
              alpha = 0.6) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 60),
    breaks = seq(0, 60, by = 20)) +
  scale_x_continuous(name = "Depth (m)",
                     breaks = seq(0, 100, by = 20)) +
  theme_classic() +
  ggtitle("Excavators") +
   theme(
        axis.title = element_text(size = 15),
        axis.text = element_text(size = 12),
        plot.title = element_text(size = 18)) +
  geom_image(data = tibble(Depth_m = 90,
                           prob = 57),
             aes(image = "chlorurus.png"),
             size = 0.30)
  
```

## exc slope newdata

```{r}
exc_nd_slope <- emmeans(exc_mod,
                          ~Aspect_descriptive,
                          type = "response") |> 
  as.data.frame()
```

## exc slope plot

```{r}
p_slope_exc_A <- 
exc_nd_slope |> 
  ggplot(aes(x = Aspect_descriptive,
             y = prob)) +
  geom_pointrange(aes(ymin = lower.HPD,
                      ymax = upper.HPD),
                  shape = 21,
                  size = 1,
                  fatten = 3,
                  color = "#E29297",
                  fill = "#E29297") +
  scale_y_continuous(Abundance~(ind.150m^-2),
                     limits = c(0, 1),
                     breaks = seq(0, 1, by = 0.5)) +
  scale_x_discrete(name = "Slope orientation") +
  theme_classic() +
  ggtitle("Excavators") +
  theme(axis.text.x = element_text(angle = 20,
                                 vjust = 0.90,
                                 hjust = 0.70,
                                 size = 12),
        axis.title = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18)) +
  geom_image(data = tibble(Aspect_descriptive = 5,
                           prob = 0.9),
             aes(image = "chlorurus.png"),
             size = 0.30)
```

## slope pairwise

```{r}
exc_mod|> emmeans(~ Aspect_descriptive,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  mutate(Exp = exp(.value)) |> 
  dplyr::select(-.chain, 
                -.value,
                -.iteration) |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  Pl = ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  dplyr::filter(Pl > 0.85 | 
           Pg > 0.85)
```

## plot pairwise

```{r}
exc_abun_slope_pair <- exc_mod|> emmeans(~ Aspect_descriptive,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  summarise(median_hdci(exp(.value),
                        .width = c(0.85, 0.95))) 
  
 p_exc_abun_slope_pair <- ggplot() + 
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = exc_abun_slope_pair|> filter(.width == 0.85),
                  linewidth = 1.7) +
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = exc_abun_slope_pair|> filter(.width == 0.95),
                  pch = 21,
                  size = 1.2,
                  fill = "#E29297",
                  linewidth = 0.7) +
  geom_hline(yintercept = 1, 
             linetype = "dashed",
             color = "red",
             linewidth = 1) +
    coord_flip() +
  theme_classic() +
  scale_x_discrete(name = "Contrast: slope orientation") +
  scale_y_continuous(name = "Scaled effect size",
                   trans = scales::log2_trans()) +
  ggtitle("Excavators") +
  theme(
        axis.title = element_text(size = 15),
        axis.text = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# SCRAPERS

## exceedance probability

```{r}
scra_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))|> 
  filter(Pl > 0.85 | 
           Pg > 0.85)
```

## scra predict

```{r}
scra_depth_pred <- scra_mod |> 
  emmeans(~ Depth_m, 
          at = depth_newdata, 
          type = "response") |> 
  as.data.frame()
```

## scra depth plot

```{r}
p_depth_scra_A <- 
scra_depth_pred  |> 
  ggplot(aes(y = prob,
             x = Depth_m)) +
    geom_point(data = fg_abun,
             aes(y = scraper),
             size = 2.5,
             shape = 21,
             color = "#BFAECF",
             fill = "#BFAECF",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#BFAECF") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#BFAECF",
              color = "#BFAECF",
              alpha = 0.6) +
  scale_y_continuous(name = "",
                       limits = c(0, 60),
    breaks = seq(0, 60, by = 20)) +
  scale_x_continuous(name = "Depth (m)",
                     breaks = seq(0, 100, by = 20)) +
  theme_classic() +
  ggtitle("Scrapers") +
   theme(axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 12),
        axis.title.x = element_text(size = 15),
        plot.title = element_text(size = 18)) +
  geom_image(data = tibble(Depth_m = 90,
                           prob = 57),
             aes(image = "scarus.png"),
             size = 0.30)
```

## scra slope newdata

```{r}
scra_nd_slope <- emmeans(scra_mod,
                          ~Aspect_descriptive,
                          type = "response") |> 
  as.data.frame()
```

## scra slope plot

```{r}
p_slope_scra_A <- 
scra_nd_slope |> 
  ggplot(aes(x = Aspect_descriptive,
             y = prob)) +
  geom_pointrange(aes(ymin = lower.HPD,
                      ymax = upper.HPD),
                  shape = 21,
                  size = 1,
                  fatten = 3,
                  color = "#BFAECF",
                  fill = "#BFAECF") +
  scale_y_continuous(name = "",
                     limits = c(0,5),
                     breaks = seq(0,5, by = 2.5)) +
  scale_x_discrete(name = "Slope orientation") +
  theme_classic() +
  ggtitle("Scrapers") +
  theme(axis.text.x = element_text(angle = 20,
                                 vjust = 0.90,
                                 hjust = 0.70,
                                 size = 12),
        axis.title = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18)) +
  geom_image(data = tibble(Aspect_descriptive = 5,
                           prob = 4.8),
             aes(image = "scarus.png"),
             size = 0.30)
```

## slope pairwise

```{r}
scra_mod|> emmeans(~ Aspect_descriptive,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  mutate(Exp = exp(.value)) |> 
  dplyr::select(-.chain, 
                -.value,
                -.iteration) |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  Pl = ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  dplyr::filter(Pl > 0.85 | 
           Pg > 0.85)
```

## plot pairwise

```{r}
scra_abun_slope_pair <- scra_mod|> emmeans(~ Aspect_descriptive,
                         type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> 
  summarise(median_hdci(exp(.value),
                        .width = c(0.85, 0.95))) 
  
 p_scra_abun_slope_pair <- ggplot() + 
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = scra_abun_slope_pair|> filter(.width == 0.85),
                  linewidth = 1.7) +
  geom_pointrange(aes(y = y, 
                      x = contrast, 
                      ymin = ymin, 
                      ymax = ymax),
                  data = scra_abun_slope_pair|> filter(.width == 0.95),
                  pch = 21,
                  size = 1.2,
                  fill = "#BFAECF",
                  linewidth = 0.7) +
  geom_hline(yintercept = 1, 
             linetype = "dashed",
             color = "red",
             linewidth = 1) +
    coord_flip() +
  theme_classic() +
  scale_x_discrete(name = "") +
  scale_y_continuous(name = "Scaled effect size",
                   trans = scales::log2_trans()) +
  ggtitle("Scrapers") +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# COMBINED DEPTH PLOT

```{r}
p_abun_all <-
(p_depth_allherbs_A + p_depth_brow_A) /
  (p_depth_crop_A + p_depth_det_A) /
  (p_depth_exc_A + p_depth_scra_A) + 
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 15))
```

## ggsave

```{r}
ggsave("Fig. 3. abun_depth.jpeg",
       plot = p_abun_all, 
       dpi = 600, 
       height = 9.5, 
       width = 9.5, 
       units = "in")
```

# COMBINED SLOPE PLOT

```{r}
p_abun_slope_all <-
(p_slope_allherbs_A + p_slope_brow_A) /
  (p_slope_crop_A + p_slope_det_A) /
  (p_slope_exc_A + p_slope_scra_A) + 
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 15))
```

## ggsave

```{r}
ggsave("Fig. 4. abun_slope.jpeg",
       plot = p_abun_slope_all, 
       dpi = 600, 
       height = 10, 
       width = 10, 
       units = "in")
```

# COMBINE SLOPE PAIRWISE

```{r}
p_fg_abun_slope_pair <- 
(p_brow_abun_slope_pair + p_crop_abun_slope_pair + p_det_abun_slope_pair) /
  (p_exc_abun_slope_pair + p_scra_abun_slope_pair) +
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 15))
```

## ggsave

```{r}
ggsave("Fig. S2. fg_abun_slope_pair.jpeg",
       plot = p_fg_abun_slope_pair, 
       dpi = 600, 
       height = 7, 
       width = 10, 
       units = "in")
```