---
title: "Tests_ZI_Negbinom"
format: html
editor: visual
---

# ALL HERBIVORES

## define formula

```{r}
herbs_form_zi <- 
  bf(herbs ~ Depth_m +
       Aspect_descriptive +
       (1 | Site) + 
       (1 | Habitat),
     family = zero_inflated_negbinomial(link = "log"))
```

## get prior

```{r}
get_prior(herbs_form_zi, data = fg_abun)
```


## Weakly informative priors

```{r}
herb_priors_zi <- prior(normal(1.2, 2), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 2), class = "sd") +
  prior(logistic(0, 1), class = "zi")
```

## Herbs prior only

```{r}
#| cache: true
herbs_prior_mod_zi <- brm(herbs_form_zi,
                    data = fg_abun,
                    prior = herb_priors_zi,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## Prior evaluation

```{r}
herbs_prior_mod_zi |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## Fit model

```{r}
#| cache: true
herbs_mod_zi <- update(herbs_prior_mod_zi,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## chain diagnostics

```{r}
par_herb_zi <- herbs_mod_zi |>  
  get_variables() |> 
  str_subset("^b_.*")

# trace
herbs_mod_zi|> mcmc_plot(type = "trace",
                         par =par_herb_zi)

# autocorr
herbs_mod_zi  |> mcmc_plot(type = "acf_bar",
                         par = par_herb_zi)

# rhat
herbs_mod_zi |> mcmc_plot(type = "rhat_hist")

# ess
herbs_mod_zi |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
herbs_resids_zi <- make_brms_dharma_res(herbs_mod_zi)

# qqplot
crop_resids |> testUniformity()

# residplot
herbs_resids_zi |> plotResiduals()

# testdisp
herbs_resids_zi |> testDispersion()
```

# CROPPERS

## Define formula

```{r}
crop_formula_zi <- 
  bf(cropper ~ Depth_m +
       Aspect_descriptive +
       (1| Site) +
       (1 | Habitat),
     family = zero_inflated_negbinomial(link = "log"))
```

## Weakly informative priors

```{r}
crop_priors_zi <- prior(normal(1.2, 2), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 2), class = "sd") +
  prior(logistic(0, 1), class = "zi")
```

## crop prior only

```{r}
#| cache: true
crop_prior_mod_zi <- brm(crop_formula_zi,
                    data = fg_abun,
                    prior = crop_priors_zi,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

# Fit model

```{r}
#| cache: true
crop_mod_zi <- update(crop_prior_mod_zi,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## chain diagnostics

```{r}
par_crop_zi <- crop_mod_zi |>  
  get_variables() |> 
  str_subset("^b_.*")

# trace
crop_mod_zi|> mcmc_plot(type = "trace",
                         par =par_crop_zi)

# autocorr
crop_mod_zi  |> mcmc_plot(type = "acf_bar",
                         par = par_crop_zi)

# rhat
crop_mod_zi |> mcmc_plot(type = "rhat_hist")

# ess
crop_mod_zi |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
crop_resids_zi <- make_brms_dharma_res(crop_mod_zi)

# qqplot
crop_resids_zi |> testUniformity()

# residplot
crop_resids_zi |> plotResiduals()

# testdisp
crop_resids_zi |> testDispersion()
```

# DETRITIVORES

## Define formula

```{r}
det_form_zi <- 
  bf(detritivore ~ Depth_m +
       Aspect_descriptive +
       (1 | Site) +
       (1 | Habitat),
     family = zero_inflated_negbinomial(link = "log"))
```

## weakly informative priors

```{r}
det_priors_zi <- prior(normal(0.5, 0.8), class = "Intercept") +
  prior(normal(0, 2.2), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0 , 0.8), class = "sd") +
  prior(logistic(0, 1), class = "zi")
```

## Dets prior only


```{r}
#| cache: true
det_prior_mod_zi <- brm(det_form_zi,
                    data = fg_abun ,
                    prior = det_priors_zi,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 1000)
```

# Fit model

```{r}
#| cache: true
det_mod_zi <- update(det_prior_mod_zi,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## chain diagnoistcs

```{r}
par_det_zi <- det_mod_zi |>  
  get_variables() |> 
  str_subset("^b_.*")
# trace
det_mod_zi |> mcmc_plot(type = "trace",
                         par = par_det_zi)
# autocorr
det_mod_zi  |> mcmc_plot(type = "acf_bar",
                         par = par_det_zi)
# rhat
det_mod_zi |> mcmc_plot(type = "rhat_hist")
# ess
det_mod_zi  |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
det_resids_zi <- make_brms_dharma_res(det_mod_zi)
# qqplot
det_resids_zi |> testUniformity()
# residplot
det_resids_zi |> plotResiduals()
# testdisp
det_resids_zi |> testDispersion()
```

# SCRAPERS

## Define formula

```{r}
scra_form_zi <- 
  bf(scraper ~ Depth_m +
       Aspect_descriptive +
       (1| Site) +
       (1 | Habitat),
     family = zero_inflated_negbinomial(link = "log"))
```

## weakly informative priors

```{r}
scra_priors_zi <- prior(normal(2, 1), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1), class = "sd") +
  prior(logistic(0, 1), class = "zi")
```

## scra prior only


```{r}
#| cache: true
scra_prior_mod_zi <- brm(scra_form_zi,
                    data = fg_abun ,
                    prior = scra_priors_zi,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 1000)
```

# Fit model

```{r}
#| cache: true
scra_mod_zi <- update(scra_prior_mod_zi,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## residuals

```{r}
scra_resids_zi <- make_brms_dharma_res(scra_mod_zi)
# qqplot
scra_resids_zi |> testUniformity()
# residplot
scra_resids_zi |> plotResiduals()
# testdisp
scra_resids_zi |> testDispersion()
```

# EXCAVATORS

## Define formula

```{r}
exc_form_zi <- 
  bf(excavator ~ Depth_m +
       Aspect_descriptive +
       (1| Site) +
       (1 | Habitat),
     family = zero_inflated_negbinomial(link = "log"))
```

## weakly informative priors

```{r}
exc_priors_zi <- prior(normal(2.3, 2.7), class = "Intercept") +
  prior(normal(0, 0.2), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 2.7), class = "sd") +
  prior(logistic(0, 1), class = "zi")
```

## scra prior only


```{r}
#| cache: true
exc_prior_mod_zi <- brm(exc_form_zi,
                    data = fg_abun ,
                    prior = exc_priors_zi,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 1000)
```

# Fit model

```{r}
#| cache: true
exc_mod_zi <- update(exc_prior_mod_zi,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## Residuals

```{r}
exc_zi_resids <- make_brms_dharma_res(exc_mod_zi) 
# qqplot
exc_zi_resids |> testUniformity()
# residplot
exc_zi_resids |> plotResiduals()
# testdisp
exc_zi_resids |> testDispersion()
```